---
title: "Uncanny Valley"
author: "Kimberly A. Brink"
date: '`r format(Sys.Date(),"%B %d, %Y")`'
output: html_document
---
###Variables
Uncanny Valley 1: Do you feel the robot is creepy?

Uncanny Valley 2: Does the robot make you feel weird?

Uncanny Valley 3: Would you want to play with the robot?

Agency 1: Can the robot do things on purpose?

Agency 2: When the robot moves does it choose to move?

Internal State 1: Does the robot think for itself?

Internal State 2: Does the robot know the difference between good and bad?

Internal State 3: Would the robot feel pain?

Internal State 4: Does the robot have feelings?

Internal State 5: Would the robot feel scared?

Internal State 6: Would the robot feel hungry?

Human-likeness 1: Is this robot like a human?

Exploratory 1: Does the robot know it's a robot?
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figures/', dev=c('png','postscript'), fig.width = 8, fig.height = 8, echo=FALSE, warning=FALSE, message=FALSE)
```

```{r install_libraries}
#library(extrafont)
library(lubridate)
library(Hmisc)
#library(knitr)
options("scipen"=100, "digits"= 4)

```

```{r standard_error}
s.error <- function(x) sd(x,na.rm=TRUE)/sqrt(length(x))
```

```{r load_file}
#filename <- "/Volumes/lsa-research01/ALL STUDIES/Current Studies/Uncanny Valley/UV - UV - First Robot.sav"
filename <- "/Volumes/lsa-research01/ALL STUDIES/Current Studies/Uncanny Valley/1.0/UV - Data.sav"
UV <- spss.get(filename,datevars=c("DOB","DOT"),use.value.labels=FALSE)
UV <- UV[which((UV$Order=='1')&(UV$Condition==1)|(UV$Order=='2')&(UV$Condition==2)|(UV$Order=='3')&(UV$Condition==1)|(UV$Order=='4')&(UV$Condition==2)),]
```

```{r calculate_variables}
UV$Age = (year(as.period(interval(UV$DOB, UV$DOT)))*12) + month(as.period(interval(UV$DOB, UV$DOT))) + (day(as.period(interval(UV$DOB, UV$DOT)))/30)
UV$UV_index = (UV$UV1 + UV$UV2) / 2
UV$CondByAge = UV$Condition * UV$Age
UV$AgeYears = UV$Age/12
UV$AgeGroup = factor(ifelse(UV$Age<=72, "1", ifelse(UV$Age<=108, "2", ifelse(UV$Age<=144, "3", "4"))))
UV$Robot = ifelse(UV$Condition==1,"Kaspar Back","Kaspar Front")
```

###Demographics.
There are `r length(UV$SubID)` participants.

```{r}
#UV = UV[ which( UV$Condition!=3 ), ]
UV = UV[ which( UV$Age <= 216 & UV$Age >= 30 ), ]
UV[ UV == 999 ] <- NA

isGirl <- UV$Sex == "1"

attach(UV)
```
After reducing participants outside of the age range, there are `r length(UV$SubID)` participants.

The average age of the sample is `r round(mean(Age)/12, digits = 2)` years.

The minimum age of the sample is `r round(min(Age)/12, digits = 2)` years.

The maximum age of the sample is `r round(max(Age)/12, digits = 2)` years

There are `r sum(isGirl)` (`r (sum(isGirl)/length(UV$SubID))*100`%) females in the sample.

The most recent date of test was `r max(DOT)`.

The first date of test was `r min(DOT)`.

```{r plot_settings}
responseAxis <- 1.3
responseAxis2 <- 1.9
ageAxis <- 2
humanColor = 'blue'
machineColor = 'red'
plotFill = 'white'
titleSize = 3
titleSizeSmall = 2
titleSizeExtraSmall = 1.5
font = "Georgia"
lineWidth = 5
```

```{r DOT_hist, fig.width=8, fig.height=8}
hist(DOT, breaks = "months", freq = TRUE)
```

#Bar Charts and ANOVAs

```{r barByAge_function}
barByAge <-function(v,data,title){
means <- aggregate(v~Robot+AgeGroup,data,mean)
se <- aggregate(v~Robot+AgeGroup,data,s.error)

meansM<-matrix(means$v,ncol=4,byrow=FALSE)
se<-matrix(se$v,ncol=4,byrow=FALSE)
colnames(meansM) <- c('<6','6-9','9-12','>12')
rownames(meansM) <- levels(factor(means$Robot))
#means <- as.table(means)
meansR <- round(meansM,2)
g.range = range(0,ceiling(max(means$v)+1))

plot.new()
barCenters <- barplot(meansM, col=c("darkblue","red"), legend = rownames(meansM), beside = TRUE, ylim=g.range, yaxt='n',las=1,main=title)
axis(2, at = c(0:4), labels = c('','No', 'A little bit', 'A medium amount', 'A lot'))
arrows(barCenters, meansM-se, barCenters, meansM+se, lwd = 2, length=0.05, angle=90, code=3)
text(barCenters,meansM+1.5*se,label=meansR)
}
```

```{r barByAge_UV1}
barByAge(UV$UV1,UV, "Do you feel the robot is creepy?")
barByAge(UV$UV2,UV, "Does the robot make you feel weird?")
barByAge(UV$UV3,UV, "Would you want to play with the robot?")
barByAge(UV$UV_index,UV,"UV Composite")
barByAge(UV$IS1,UV,"Does the robot think for itself?")
barByAge(UV$IS2,UV,"Does the robot know the difference between good and bad?")
barByAge(UV$IS3,UV,"Would the robot feel pain?")
barByAge(UV$IS4,UV,"Does the robot have feelings?")
barByAge(UV$IS5,UV,"Would the robot feel scared?")
barByAge(UV$IS6,UV,"Would the robot feel hungry?")
barByAge(UV$A1,UV,"Can the robot do things on purpose?")
barByAge(UV$A2,UV,"When the robot moves does it choose to move?")
barByAge(UV$HL1,UV,"Is this robot like a human?")
barByAge(UV$E1,UV,"Does the robot know it's a robot?")
```

#Scatter plots and fit lines 
Thoughts (IS1), Pain (IS3), Emotions (IS4), Hunger (IS6), Fear (IS5), Choice (A2) for Kaspar Back and Front by Age

```{r scatter_plot_6, fig.width=20, fig.height=19}
#```{r scatter_plot_6, fig.width=20, fig.height=28}
plot.new()

#Scatter plots and fit lines for Thoughts (IS1) by Age

par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0.5,1), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0.7,1), new=TRUE)
plot(AgeYears, jitter(IS1), main = "Does the robot think for itself?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis2)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(AgeYears, jitter(IS1), col = humanColor, cex = ageAxis)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis2)
abline(lm(IS1~AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(IS1~AgeYears)
#fit <- lm(IS1~Age+I(Age^2), UV)
#fit2line <- predict(fit, UV.frame(dist = -10:160))
#lines(-10:160, fit2line, col = humanColor)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+2.2, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)

#Scatter plots and fit lines for Pain (IS3) by Age

# par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.7,1), new=TRUE)
# plot(Age, jitter(IS3), main = "Would the robot feel pain?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis2)
# u <- par("usr") 
# rect(u[1], u[3], u[2], u[4], col = plotFill)
# points(Age, jitter(IS3), col = humanColor, cex = ageAxis)
# axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis2)
# abline(lm(IS3~Age), col = humanColor, lwd = lineWidth)
# fit <- lm(IS3~Age)
# a <- summary(fit)$coefficient['(Intercept)','Estimate']
# b <- summary(fit)$coefficient['Age','Estimate']
# r2 <- format(summary(fit)$adj.r.squared, digits = 3)
# f <- summary(fit)$fstatistic
# p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
# p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
# text(((2.5-a)/b)+40, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)


#Scatter plots and fit lines for Emotions (IS4) by Age

par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.5,1), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.7,1), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0.4,0.69), new=TRUE)
plot(AgeYears, jitter(IS4), main = "Does the robot have feelings?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis2)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(AgeYears, jitter(IS4), col = humanColor, cex = responseAxis2)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis2)
abline(lm(IS4~AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(IS4~AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+2.8, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)


#Scatter plots and fit lines for Hunger (IS6) by Age

par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0,0.5), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0.4,0.69), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.4,0.69), new=TRUE)
plot(AgeYears, jitter(IS6), main = "Would the robot feel hungry?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis2)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(AgeYears, jitter(IS6), col = humanColor, cex = responseAxis2)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis2)
abline(lm(IS6~AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(IS6~AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+2.7, 2.5,bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)

#Scatter plots and fit lines for Fear (IS5) by Age

par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0,0.5), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.4,0.69), new=TRUE)
#par(mar=c(4.5,5,2,2)+0.1, fig=c(0,0.5,0.1,0.39), new=TRUE)
plot(AgeYears, jitter(IS5), main = "Would the robot feel scared?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis2)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(AgeYears, jitter(IS5), col = humanColor, cex = responseAxis2)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis2)
abline(lm(IS5~AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(IS5~AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+3.2, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)

#Scatter plots and fit lines for Choice (A2) by Age

# par(mar=c(4.5,5,2,2)+0.1, fig=c(0.5,1,0.1,0.39), new=TRUE)
# plot(Age, jitter(A2), main = "Does the robot choose to move?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis)
# u <- par("usr") 
# rect(u[1], u[3], u[2], u[4], col = plotFill)
# points(Age, jitter(A2), col = humanColor, cex = responseAxis)
# axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
# abline(lm(A2~Age), col = humanColor, lwd = lineWidth)
# fit <- lm(A2~Age)
# a <- summary(fit)$coefficient['(Intercept)','Estimate']
# b <- summary(fit)$coefficient['Age','Estimate']
# r2 <- format(summary(fit)$adj.r.squared, digits = 3)
# f <- summary(fit)$fstatistic
# p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
# p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
# text(((2.5-a)/b)+40, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)
```



#Scatterplot for Exploratory Question (E1)
```{r scatter_E1}

plot.new()
par(mar=c(5,5,5,5)+0.1)
plot(AgeYears, jitter(E1), main = "Does the robot know it's a robot?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', cex.main = titleSize, cex.axis = ageAxis, cex.lab = ageAxis, col = humanColor, cex = responseAxis)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(AgeYears, jitter(E1), col = humanColor, cex = responseAxis)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
abline(lm(E1~AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(E1~AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+3.5, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = ageAxis)
```

#Scatterplot for Morality (IS2)
```{r scatter_Morality}
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

plot.new()
par(mar=c(5,5,5,5)+0.1)
plot(KasparFront$AgeYears, jitter(KasparFront$IS2), main = "Does this robot know the\n difference between good and bad?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', col = humanColor, cex.main = titleSizeSmall, cex.axis = responseAxis, cex.lab= ageAxis)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(KasparFront$AgeYears, jitter(KasparFront$IS2), col = humanColor)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
abline(lm(KasparFront$IS2~KasparFront$AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(KasparFront$IS2~KasparFront$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparFront$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(10, 2.4, bquote(paste( R^2 == .(r2), ', p '== .(p))), col = humanColor, cex = responseAxis)

points(KasparBack$AgeYears, jitter(KasparBack$IS2), col = machineColor)
abline(lm(KasparBack$IS2~KasparBack$AgeYears), col = machineColor, lwd = lineWidth)
fit <- lm(KasparBack$IS2~KasparBack$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparBack$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+1.7, 2.6, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = machineColor, cex = responseAxis)

legend( 'topright',c( "Machine-like", "Human-like" ), col = c( "Red","Blue" ), lwd = lineWidth, bg = 'white', inset = .025) 

```

##Test of interaction between Morality, Age, and Robot appearance

```{r ixn_Morality}
mIxnTest <- lm(IS2 ~ AgeYears*Condition, UV=UV)

varTest = 'AgeYears:Condition'
ixnBeta = summary(mIxnTest)$coefficient[varTest,'Estimate']
ixnDF = length(unique(Condition))-1
ixnT <- summary(mIxnTest)$coefficient[varTest,'t value']
ixnP <- round(summary(mIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ixnP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ixnP)))

varTest = 'AgeYears'
ageBeta = summary(mIxnTest)$coefficient[varTest,'Estimate']
ageDF = length(unique(Condition))-1
ageT <- summary(mIxnTest)$coefficient[varTest,'t value']
ageP <- round(summary(mIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ageP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ageP)))

varTest = 'Condition'
conBeta = summary(mIxnTest)$coefficient[varTest,'Estimate']
conDF = length(unique(Condition))-1
conT <- summary(mIxnTest)$coefficient[varTest,'t value']
conP <- round(summary(mIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
conP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
```
There was a significant interaction between child's age and robot appearance on children's report of moral behavior, $\beta$ = `r ixnBeta`, *t*(`r ixnDF`) = `r ixnT`, *p* < `r ixnP`.

There was a significant main effect of child's age on children's report of moral behavior, $\beta$ = `r ageBeta`, *t*(`r ageDF`) = `r ageT`, *p* < `r ageP`.

There was a significant main effect of robot appearance on children's report of moral behavior, $\beta$ = `r conBeta`, *t*(`r conDF`) = `r conT`, *p* < `r conP`.

#Comparing Uncanny Valley measures for Kaspar Back and Kaspar Front
##T-Test for each Uncanny measure for all participants
```{r ttest_UVAll}
ageCutoff = 144 #months
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

ttest_UV1 = t.test(KasparFront$UV1,KasparBack$UV1,paired=FALSE)
ttest_UV2 = t.test(KasparFront$UV2,KasparBack$UV2,paired=FALSE)
ttest_UV3 = t.test(KasparFront$UV3,KasparBack$UV3,paired=FALSE)
ttest_UVindex = t.test(KasparFront$UV_index,KasparBack$UV_index,paired=FALSE)
```
There is not a significant difference in children's reports of creepiness for the two different robots, *t*(`r ttest_UV1$parameter`) = `r ttest_UV1$statistic`, *p* = `r ttest_UV1$p.value`.

There is not a significant difference in children's reports of feelings of weirdness for the two different robots, *t*(`r ttest_UV2$parameter`) = `r ttest_UV2$statistic`, *p* = `r ttest_UV2$p.value`.

There is not a significant difference in children's reports of wanting to play with the two different robots, *t*(`r ttest_UV3$parameter`) = `r ttest_UV3$statistic`, *p* = `r ttest_UV3$p.value`.

There is not a significant difference in the Uncanny Valley composite for the two different robots, *t*(`r ttest_UVindex$parameter`) = `r ttest_UVindex$statistic`, *p* = `r ttest_UVindex$p.value`.

##T-Test for each Uncanny measure for all participants older than `r ageCutoff/12` years
```{r ttest_UV126}
KasparFrontOld = KasparFront[ which( KasparFront$Age>=ageCutoff), ]
KasparBackOld = KasparBack[ which( KasparBack$Age>=ageCutoff) , ]

KasparFrontOld = KasparFrontOld[ which( KasparFrontOld$UV2!='NA'), ]
KasparBackOld = KasparBackOld[ which( KasparBackOld$UV2!='NA') , ]

ttest_UV1 = t.test(KasparFrontOld$UV1,KasparBackOld$UV1,paired=FALSE)
ttest_UV2 = t.test(KasparFrontOld$UV2,KasparBackOld$UV2,paired=FALSE)
ttest_UV3 = t.test(KasparFrontOld$UV3,KasparBackOld$UV3,paired=FALSE)
ttest_UVindex = t.test(KasparFrontOld$UV_index,KasparBackOld$UV_index,paired=FALSE)
```
There is not a significant difference in children's reports of creepiness for the two different robots, *t*(`r ttest_UV1$parameter`) = `r ttest_UV1$statistic`, *p* = `r ttest_UV1$p.value`.

There is not a significant difference in children's reports of feelings of weirdness for the two different robots, *t*(`r ttest_UV2$parameter`) = `r ttest_UV2$statistic`, *p* = `r ttest_UV2$p.value`.

There is not a significant difference in children's reports of wanting to play with the two different robots, *t*(`r ttest_UV3$parameter`) = `r ttest_UV3$statistic`, *p* = `r ttest_UV3$p.value`.

There is not a significant difference in the Uncanny Valley composite for the two different robots, *t*(`r ttest_UVindex$parameter`) = `r ttest_UVindex$statistic`, *p* = `r ttest_UVindex$p.value`.

##Barplot for Uncanny Valley (UV1)
```{r bar_UV1, fig.height=7, fig.width=5.5}
KasparFrontOld = KasparFrontOld[ which( KasparFrontOld$UV1!='NA'), ]
KasparBackOld = KasparBackOld[ which( KasparBackOld$UV1!='NA') , ]

KFront = mean(KasparFrontOld$UV1)
KBack = mean(KasparBackOld$UV1)
KFront.se = sd(KasparFrontOld$UV1)/sqrt(length(KasparFrontOld$UV1))
KBack.se = sd(KasparBackOld$UV1)/sqrt(length(KasparBackOld$UV1))

names <- c(paste("Machine-like (N = ", length(KasparBackOld$UV1),")",sep=""), paste("Human-like (N = ", length(KasparFrontOld$UV1),")",sep=""))
means <- c(KBack, KFront)
se <- c(KBack.se,KFront.se)

plot.new()
barCenters <- barplot(means, ylim=c(0,ceiling(max(means+se))),names.arg=names,ylab="Response",las=1, lwd = 4, col=c("red","blue"),main=paste("Do you think the robot is creepy? \n(Age >", ageCutoff/12, "years)",""),yaxt = 'n',cex.main = titleSizeExtraSmall)
axis(2, at = c(0:4), labels = c('','No', 'A little bit', 'A medium amount', 'A lot'))
arrows(barCenters, means-se, barCenters, means+se,lwd=lineWidth,angle=90,code=3)
```

##Test of difference in Uncanny Valley (UV1) by Robot appearance
There is not a significant difference in children's reports of creepiness for the two different robots, *t*(`r ttest_UV1$parameter`) = `r ttest_UV1$statistic`, *p* = `r ttest_UV1$p.value`.

##Scatter plot for Uncanny Valley (UV1)
```{r scatter_UV1}
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

plot.new()
par(mar=c(5,5,5,5)+0.1)
plot(KasparFront$AgeYears, jitter(KasparFront$UV1), main = "Do you think this robot is creepy?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', col = humanColor, cex.main = titleSizeSmall, cex.axis = responseAxis, cex.lab = ageAxis)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(KasparFront$AgeYears, jitter(KasparFront$UV1), col = humanColor)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
abline(lm(KasparFront$UV1~KasparFront$AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(KasparFront$UV1~KasparFront$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparFront$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)-8, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = responseAxis)

points(KasparBack$AgeYears, jitter(KasparBack$UV1), col = machineColor)
abline(lm(KasparBack$UV1~KasparBack$AgeYears), col = machineColor, lwd = lineWidth)
fit <- lm(KasparBack$UV1~KasparBack$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparBack$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+8, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = machineColor, cex = responseAxis)

legend('topright',c("Machine-like", "Human-like"), col = c("Red","Blue"), lwd = lineWidth, bg = 'white', inset = .025)
```

##Test of interaction between Uncanny Valley (UV1), Age, and Robot appearance
```{r ixn_UV1}
uv1IxnTest <- lm(UV1 ~ AgeYears*Condition, UV=UV)
#summary(uvIxnTest)

varTest = 'AgeYears:Condition'
ixnBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
ixnDF = length(unique(Condition))-1
ixnT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
ixnP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ixnP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ixnP)))

varTest = 'AgeYears'
ageBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
ageDF = length(unique(Condition))-1
ageT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
ageP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ageP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ageP)))

varTest = 'Condition'
conBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
conDF = length(unique(Condition))-1
conT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
conP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
conP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,conP)))
```
There was not a significant interaction between child's age and robot appearance on children's reports of creepiness, $\beta$ = `r ixnBeta`, *t*(`r ixnDF`) = `r ixnT`, *p* = `r ixnP`.

There was not a significant main effect of child's age on children's reports of creepiness, $\beta$ = `r ageBeta`, *t*(`r ageDF`) = `r ageT`, *p* = `r ageP`.

There was not a significant main effect of robot appearance on children's reports of creepiness, $\beta$ = `r conBeta`, *t*(`r conDF`) = `r conT`, *p* = `r conP`.

##Barplot for Uncanny Valley (UV2)
```{r bar_UV2, fig.width=5.5, fig.height=7}
KFront = mean(KasparFrontOld$UV2)
KBack = mean(KasparBackOld$UV2)
KFront.se = sd(KasparFrontOld$UV2)/sqrt(length(KasparFrontOld$UV2))
KBack.se = sd(KasparBackOld$UV2)/sqrt(length(KasparBackOld$UV2))

names <- c(paste("Machine-like (N = ", length(KasparBackOld$UV2),")",sep=""), paste("Human-like (N = ", length(KasparFrontOld$UV2),")",sep=""))
means <- c(KBack, KFront)
se <- c(KBack.se,KFront.se)

plot.new()
barCenters <- barplot(means, ylim=c(0,ceiling(max(means+se))),names.arg=names,ylab="Response",las=1, lwd = 4, col=c("red","blue"),main=paste("Does this robot make you feel weird? \n(Age >", ageCutoff/12, "years)",""),yaxt = 'n',cex.main = titleSizeExtraSmall)
axis(2, at = c(0:4), labels = c('','No', 'A little bit', 'A medium amount', 'A lot'))
arrows(barCenters, means-se, barCenters, means+se,lwd=2,angle=90,code=3)
```

##Test of difference in Uncanny Valley (UV2) by Robot appearance
There is not a significant difference in children's reports of feelings of weirdness for the two different robots, *t*(`r ttest_UV2$parameter`) = `r ttest_UV2$statistic`, *p* = `r ttest_UV2$p.value`.

##Scatter plot for Uncanny Valley (UV2)
```{r scatter_UV2}
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

plot.new()
par(mar=c(5,5,5,5)+0.1)
plot(KasparFront$AgeYears, jitter(KasparFront$UV2), main = "Does this robot make you feel weird?", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', col = humanColor, cex.main = titleSizeSmall, cex.axis = responseAxis, cex.lab = ageAxis)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(KasparFront$AgeYears, jitter(KasparFront$UV2), col = humanColor)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
abline(lm(KasparFront$UV2~KasparFront$AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(KasparFront$UV2~KasparFront$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparFront$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(10.3, 2.5, bquote(paste( R^2 == .(r2), ', p '== .(p))), col = humanColor, cex = responseAxis)

points(KasparBack$AgeYears, jitter(KasparBack$UV2), col = machineColor)
abline(lm(KasparBack$UV2~KasparBack$AgeYears), col = machineColor, lwd = lineWidth)
fit <- lm(KasparBack$UV2~KasparBack$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparBack$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(5.7, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = machineColor, cex = responseAxis)

legend('topright',c("Machine-like", "Human-like"), col = c("Red","Blue"), lwd = lineWidth, bg = 'white', inset = .025)
```

##Test of interaction between Uncanny Valley (UV2), Age, and Robot appearance
```{r ixn_UV2}
uvIxnTest <- lm(UV2 ~ AgeYears*Condition, UV=UV)
#summary(uvIxnTest)

varTest = 'AgeYears:Condition'
ixnBeta = summary(uvIxnTest)$coefficient[varTest,'Estimate']
ixnDF = length(unique(Condition))-1
ixnT <- summary(uvIxnTest)$coefficient[varTest,'t value']
ixnP <- round(summary(uvIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ixnP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ixnP)))

varTest = 'AgeYears'
ageBeta = summary(uvIxnTest)$coefficient[varTest,'Estimate']
ageDF = length(unique(Condition))-1
ageT <- summary(uvIxnTest)$coefficient[varTest,'t value']
ageP <- round(summary(uvIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ageP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ageP)))

varTest = 'Condition'
conBeta = summary(uvIxnTest)$coefficient[varTest,'Estimate']
conDF = length(unique(Condition))-1
conT <- summary(uvIxnTest)$coefficient[varTest,'t value']
conP <- round(summary(uvIxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
conP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,conP)))
```

There was not a significant interaction between child's age and robot appearance on children's reports of feelings of weirdness, $\beta$ = `r ixnBeta`, *t*(`r ixnDF`) = `r ixnT`, *p* = `r ixnP`.

There was not a significant main effect of child's age on children's reports of feelings of weirdness, $\beta$ = `r ageBeta`, *t*(`r ageDF`) = `r ageT`, *p* = `r ageP`.

There was not a significant main effect of robot appearance on children's reports of feelings of weirdness, $\beta$ = `r conBeta`, *t*(`r conDF`) = `r conT`, *p* = `r conP`.

##Barplot for Uncanny Valley (UV Index)
```{r bar_UVindex, fig.height=7, fig.width=5.5}
KasparFrontOld = KasparFrontOld[ which( KasparFrontOld$UV_index!='NA'), ]
KasparBackOld = KasparBackOld[ which( KasparBackOld$UV_index!='NA') , ]

KFront = mean(KasparFrontOld$UV_index)
KBack = mean(KasparBackOld$UV_index)
KFront.se = sd(KasparFrontOld$UV_index)/sqrt(length(KasparFrontOld$UV_index))
KBack.se = sd(KasparBackOld$UV_index)/sqrt(length(KasparBackOld$UV_index))

names <- c(paste("Machine-like (N = ", length(KasparBackOld$UV_index),")",sep=""), paste("Human-like (N = ", length(KasparFrontOld$UV_index),")",sep=""))
means <- c(KBack, KFront)
se <- c(KBack.se,KFront.se)

plot.new()
barCenters <- barplot(means, ylim=c(0,ceiling(max(means+se))),names.arg=names,ylab="Response",las=1, lwd = 4, col=c("red","blue"),main=paste("UV Index \n(Age >", ageCutoff/12, "years)",""),yaxt = 'n',cex.main = titleSizeExtraSmall)
axis(2, at = c(0:4), labels = c('','No', 'A little bit', 'A medium amount', 'A lot'))
arrows(barCenters, means-se, barCenters, means+se,lwd=lineWidth,angle=90,code=3)
```

##Test of difference in Uncanny Valley (UV Index) by Robot appearance
There is not a significant difference in children's reports of creepiness for the two different robots, *t*(`r ttest_UV1$parameter`) = `r ttest_UV1$statistic`, *p* = `r ttest_UV1$p.value`.

##Scatter plot for Uncanny Valley (UV Index)
```{r scatter_UVindex}
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

plot.new()
par(mar=c(5,5,5,5)+0.1)
plot(KasparFront$AgeYears, jitter(KasparFront$UV_index), main = "UV Index", xlab = 'Age (years)', ylab = 'Response', yaxt = 'n', col = humanColor, cex.main = titleSizeSmall, cex.axis = responseAxis, cex.lab = ageAxis)
u <- par("usr") 
rect(u[1], u[3], u[2], u[4], col = plotFill)
points(KasparFront$AgeYears, jitter(KasparFront$UV_index), col = humanColor)
axis(2, at = c(1:4), labels = c('No', 'A little bit', 'A medium amount', 'A lot'), cex.axis = responseAxis)
abline(lm(KasparFront$UV_index~KasparFront$AgeYears), col = humanColor, lwd = lineWidth)
fit <- lm(KasparFront$UV_index~KasparFront$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparFront$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)-8, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = humanColor, cex = responseAxis)

points(KasparBack$AgeYears, jitter(KasparBack$UV_index), col = machineColor)
abline(lm(KasparBack$UV_index~KasparBack$AgeYears), col = machineColor, lwd = lineWidth)
fit <- lm(KasparBack$UV_index~KasparBack$AgeYears)
a <- summary(fit)$coefficient['(Intercept)','Estimate']
b <- summary(fit)$coefficient['KasparBack$AgeYears','Estimate']
r2 <- format(summary(fit)$adj.r.squared, digits = 3)
f <- summary(fit)$fstatistic
p <- format(pf(f[1],f[2],f[3],lower.tail=F), digits = 3)
p <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,p)))
text(((2.5-a)/b)+8, 2.5, bquote(paste( R^2 == .(r2), ', p '< .(p))), col = machineColor, cex = responseAxis)

legend('topright',c("Machine-like", "Human-like"), col = c("Red","Blue"), lwd = lineWidth, bg = 'white', inset = .025)
```

##Test of interaction between Uncanny Valley (UV Index), Age, and Robot appearance
```{r ixn_UVindex}
uv1IxnTest <- lm(UV_index ~ AgeYears*Condition, UV=UV)
#summary(uvIxnTest)

varTest = 'AgeYears:Condition'
ixnBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
ixnDF = length(unique(Condition))-1
ixnT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
ixnP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ixnP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ixnP)))

varTest = 'AgeYears'
ageBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
ageDF = length(unique(Condition))-1
ageT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
ageP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
ageP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,ageP)))

varTest = 'Condition'
conBeta = summary(uv1IxnTest)$coefficient[varTest,'Estimate']
conDF = length(unique(Condition))-1
conT <- summary(uv1IxnTest)$coefficient[varTest,'t value']
conP <- round(summary(uv1IxnTest)$coefficient[varTest,'Pr(>|t|)'], digits = 3)
conP <- ifelse(p<0.001, 0.001, ifelse(p<0.01, 0.01, ifelse(p<0.05,0.05,conP)))
```
There was not a significant interaction between child's age and robot appearance on children's reports of creepiness, $\beta$ = `r ixnBeta`, *t*(`r ixnDF`) = `r ixnT`, *p* = `r ixnP`.

There was not a significant main effect of child's age on children's reports of creepiness, $\beta$ = `r ageBeta`, *t*(`r ageDF`) = `r ageT`, *p* = `r ageP`.

There was not a significant main effect of robot appearance on children's reports of creepiness, $\beta$ = `r conBeta`, *t*(`r conDF`) = `r conT`, *p* = `r conP`.


#Barplot for human likeness: Is the robot like a human?
```{r bar_HL1, fig.height=7, fig.width=5.5}
KasparFront = UV[ which( UV$Condition==2), ]
KasparBack = UV[ which( UV$Condition==1) , ]

KFront = mean(KasparFront$HL1)
KBack = mean(KasparBack$HL1,na.rm=TRUE)
KFront.se = sd(KasparFront$HL1)/sqrt(length(KasparFront$HL1))
KBack.se = sd(KasparBack$HL1,na.rm=TRUE)/sqrt(length(KasparBack$HL1))

names <- c(paste("Machine-like (N = ", length(KasparBack$HL1),")",sep=""), paste("Human-like (N = ", length(KasparFront$HL1),")",sep=""))
means <- c(KBack, KFront)
se <- c(KBack.se,KFront.se)

plot.new()
barCenters <- barplot(means, ylim=c(0,ceiling(max(means+se))),names.arg=names,ylab="Response",las=1, lwd = 4, col=c("red","blue"),main="Child report of human-likeness:\nIs this robot like a human?",yaxt = 'n',cex.main = titleSizeExtraSmall)
axis(2, at = c(0:4), labels = c('','No', 'A little bit', 'A medium amount', 'A lot'))
arrows(barCenters, means-se, barCenters, means+se,lwd=lineWidth,angle=90,code=3)
```

##T-Test for Human-Likeness for all participants
```{r ttest_HL1}
ttest_HL1 = t.test(KasparFront$HL1,KasparBack$HL1,paired=FALSE)
#`r if(show.text){"la la la"}`
```

There is a significant difference in children's reports of human-likeness for the two different robots, *t*(`r ttest_HL1$parameter`) = `r ttest_HL1$statistic`, *p* = `r ttest_HL1$p.value`.
