---
title: "Uncanny Valley - Child Development"
author: "Kimberly A. Brink"
date: "4/5/2017"
output: html_document
---

###Survey Questions

Uncanny Valley 1: Do you feel the robot is creepy?

Uncanny Valley 2: Does the robot make you feel weird?

Uncanny Valley 3: Would you want to play with the robot?

Agency 1: Can the robot do things on purpose?

Agency 2: When the robot moves does it choose to move?

Internal State 1: Does the robot think for itself?

Internal State 2: Does the robot know the difference between good and bad?

Internal State 3: Would the robot feel pain?

Internal State 4: Does the robot have feelings?

Internal State 5: Would the robot feel scared?

Internal State 6: Would the robot feel hungry?

Human-likeness 1: Is this robot like a human?

Exploratory 1: Does the robot know it's a robot?

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Manuscript Figures/', dev=c('png','postscript'), fig.width = 8, fig.height = 8, fig.keep='last', echo=FALSE, warning=FALSE, message=FALSE)
```

```{r load_libraries}
library(lubridate) #for calculating ages
library(Hmisc) #for importing SPSS
library(plyr) #for joining data frames
library(pander) #for displaying tables
library(psych)
library(QuantPsyc)
library(lsr)
library(reshape2) #melt
library(lavaan)
library(car) #reverse coding
```

```{r standard_error}
#calculates standard error (automatically removes missing values)
std.error <- function(x) sd(x,na.rm=TRUE)/sqrt(length(x))
```

```{r safe_ifelse}
#when using the original ifelse statement, the class of the variable contained in the yes/no statements is not protected. if a variable is contained in the yes/no statement, it may be converted to an illegible numerical class. "ifelse makes factors lose their levels and Dates lose their class and only their mode (numeric) is restored"

#this safe.ifelse function came from: http://stackoverflow.com/questions/6668963/how-to-prevent-ifelse-from-turning-date-objects-into-numeric-objects

#it protects both date columns and factor columns

safe.ifelse <- function(cond, yes, no) {
      class.y <- class(yes)
      if ("factor" %in% class.y) {  
        levels.y = levels(yes)
      }
      X <- ifelse(cond,yes,no)
      if ("factor" %in% class.y) {  
        X = as.factor(X)
        levels(X) = levels.y
      } else {
        class(X) <- class.y
      }
      return(X)
}
```

```{r screeplot_factanal}
#http://www.stat.cmu.edu/~cshalizi/350/2008/lectures/14/lecture-14.pdf
screeplot.factanal <- function(fa.fit,xlab="factor",ylab="eigenvalue",...) {
	# sum-of-squares function for repeated application
	sosq <- function(v) {sum(v^2)}
	# Get the matrix of loadings
	my.loadings <- as.matrix(fa.fit$loadings)
	# Eigenvalues can be recovered as sum of
	# squares of each column
	evalues <- apply(my.loadings,2,sosq)
	plot(evalues,xlab=xlab,ylab=ylab,...)
}
```

```{r part_cor_function, echo = FALSE}
#runs a partial correlation that can handle missing values
#I think I made this. I'm sure pieces came from all over.
part.cor <- function(x, y, z){
  xres <- residuals(lm(x ~ z, na.action = na.exclude))
  yres <- residuals(lm(y ~ z, na.action = na.exclude)) 
  result <- cor.test(xres, yres) 
  m = data.frame(1)
  m$estimate = result$estimate 
  m$tvalue = result$statistic 
  m$df = result$parameter
  m$p.value = result$p.value
  return(m)
}
```

```{r plot_settings}
#change plot aesthetics here
responseAxis <- 1.3 #
responseAxis2 <- 1.9
ageAxis <- 2 
humanColor =  rgb(146/255, 87/255, 160/255)#'dimgray' #color of bars and points for human-like robot
machineColor = rgb(140/255, 197/255, 69/255)#'lightgray' #color of bars and points for machine-like robot
naoColor = rgb(248/255, 154/255, 52/255)#'white' #color of bars and points for Nao
plotFill = 'white' #background of plot
titleSize = 3 #size of main label
titleSizeSmall = 2
titleSizeExtraSmall = 1.5
font = "Georgia"
lineWidth = 5
```

```{r barByAge_function}
barByAge <-function(v.back,v.front,v.nao,data,title){
  #find means of var for each age group for the machine-like robot
  means.back <- aggregate(v.back~AgeGroup,data,mean)
  #find means of variable for each age group for the human-like robot
  means.front <- aggregate(v.front~AgeGroup,data,mean) 
  #find means of variable for each age group for the human-like robot
  means.nao <- aggregate(v.nao~AgeGroup,data,mean) 
  
  #find standard error of var for each age group for the machine-like robot
  se.back <- aggregate(v.back~AgeGroup,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.front <- aggregate(v.front~AgeGroup,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.nao <- aggregate(v.nao~AgeGroup,data,std.error) 
  
  means.mat<-matrix(c(means.back$v.back,means.front$v.front,means.nao$v.nao),
                    ncol=4,
                    byrow=T)-1 #combine means into one matrix
  se.mat<-matrix(c(se.back$v.back,se.front$v.front,se.nao$v.nao),
                 ncol=4,
                 byrow=FALSE) #combine se into one matrix
  
  #label the columns by age group
  colnames(means.mat) <- c('3-5','6-8','9-11','12-18')
  colnames(se.mat) <- c('3-5','6-8','9-11','12-18')

  #label the rows by robot type
  rownames(means.mat) <- c('Machine-like','Human-like','Nao')
  rownames(se.mat) <- c('Machine-like','Human-like','Nao')

  #produce rounded values of the matrix for displaying on the plot
  means.matR <- round(means.mat,2) 

  plotData = melt(means.matR)
  seData = melt(se.mat)
  
  names(plotData) = c("Robot","Age Group",title)
  names(seData) = c("Robot","Age Group","SE")
  #title = plotData$

  plotData = join(plotData,seData)
  
  ggplot(data = plotData, aes(x = `Age Group`, y = plotData[title], fill = Robot)) + 
    geom_bar(width = .65, position=position_dodge(), stat="identity") + 
    geom_errorbar(aes(ymin=plotData[title]-SE, ymax=plotData[title]+SE),
                  width=.2, #Line weights
                  size = 2, #Width of the error bars
                  position=position_dodge(.65)) + 
    labs(x="Age (years)",y=title) + 
    theme(text = element_text(size=36,family="Tw Cen MT"), #set font
          axis.text.x = element_text(size=24), #set size of x-axis font
          axis.title.x = element_text(margin=margin(0,0,20,0)), #set position of x-axis title
          axis.text.y=element_text(angle=90, hjust=.5, size=24), #set size of y-axis text
          axis.title.y=element_text(margin=margin(0,20,0,0)), #set position of y-axis title
          legend.background = element_rect(), #empty box legend
          legend.key.size = unit(2, "cm"), #set size of boxes for legend
          legend.position="bottom") + #set position of legend at bottom
  scale_y_continuous(limits = c(0,3), #set min and max of y-axis
                     breaks=0:3, #set y continuous to 4 tick marks at 0,1,2,3
                     labels=c('Not at all', 'A little bit', 'A medium amount', 'A lot'), #set labels
                     expand = waiver()) #I have no idea
  
}
```

```{r load_file}
#library Hmisc
#load SPSS data file
filename <- "/Volumes/lsa-research01/ALL STUDIES/Current Studies/Uncanny Valley/1.0/UV - Data.sav"
UV.original <- spss.get(filename,datevars=c("DOB","DOT"),use.value.labels=F) #label DOB and DOT as date variables and import numerical values not string values for variables
```

```{r formatting}
#library plyr
#exclude orders 3 and where both conditions were presented together (leaving only between subjects for analysis)
UV.original <- UV.original[UV.original$Order==1|UV.original$Order==2|is.na(UV.original$Order),] 

UV.original = UV.original[which(!is.na(UV.original$SubID)),] #remove empty observations

UV.original$Age = NULL #remove experiementer entered age (will calculate later)
UV.original$AgeGroup = NULL #remove experiementer entered age (will calculate later)
UV.original$AgeYear = NULL #remove experiementer entered age (will calculate later)
UV.original$COMME0 = NULL #remove empty variable
names(UV.original)[names(UV.original) == 'VAR00001'] <- 'Comments' #name unnamed variable
names(UV.original)[names(UV.original) == 'PA11'] <- 'PQ11' #correct name of variable

#original data set was created in long format, the following code converts it to short format
#each participant had an observation for either the machine-like robot or human-like robot, then they had a set of answers about Nao. This makes sure all answers about robots are included in one observation.

#separate answers about each robot into separate data frames
UV.Nao <- UV.original[UV.original$Condition==3,] 
UV.Front <- UV.original[UV.original$Condition==2,] 
UV.Back <- UV.original[UV.original$Condition==1,] 

#remove empty observations (that would have somehow magically slipped by when I removed them before)
UV.Nao = UV.Nao[which(!is.na(UV.Nao$SubID)),] 
UV.Front = UV.Front[which(!is.na(UV.Front$SubID)),] 
UV.Back = UV.Back[which(!is.na(UV.Back$SubID)),] 

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Nao) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Nao","UV2.Nao","UV3.Nao","A1.Nao","A2.Nao","IS1.Nao","IS2.Nao","IS3.Nao","IS4.Nao","IS5.Nao","IS6.Nao","HL1.Nao","E1.Nao","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#the variables below are typically empty for Nao and not robot specific (they are a parent survey about experience with robots and technology), they can be copied over from UV.Front and UV.Back where they are always filled in
#if these variables are left in UV.Nao they cause problems with joins later
#the same subid may have empty data for these variables for the Nao dataset but not the UV.Front or UV.Back datasets, which causes these variables to be incorrectly copied over during the join
UV.Nao=UV.Nao[,!(names(UV.Nao) %in% c("Sex","DOB","DOT","Order","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments"))]

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Front) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Front","UV2.Front","UV3.Front","A1.Front","A2.Front","IS1.Front","IS2.Front","IS3.Front","IS4.Front","IS5.Front","IS6.Front","HL1.Front","E1.Front","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Back) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Back","UV2.Back","UV3.Back","A1.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back","IS4.Back","IS5.Back","IS6.Back","HL1.Back","E1.Back","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#condition is no longer needed (this information is kept in the variable names)
UV.Nao$Condition = NULL
UV.Back$Condition = NULL
UV.Front$Condition = NULL

UV.NB <- join( UV.Back,UV.Nao ) #combine observations about Nao and observations about the machine-like robot by subject ID
UV.NF <- join( UV.Front,UV.Nao ) #combine observations about Nao and observations about the machine-like robot by subject ID
UV.Total <- merge( UV.NB,UV.NF,by="SubID",all.x=T,all.y=T ) #put all the observations together into one data frame

#copy over variables that do not have a ".x" or ".y" on their name
UV = UV.Total[c("SubID","UV1.Front","UV2.Front","UV3.Front","A1.Front","A2.Front","IS1.Front","IS2.Front","IS3.Front","IS4.Front","IS5.Front","IS6.Front","HL1.Front","E1.Front","UV1.Back","UV2.Back","UV3.Back","A1.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back","IS4.Back","IS5.Back","IS6.Back","HL1.Back","E1.Back")]

#copy over variables with a ".x" or ".y" but remove that from the end of the variable name
for (var in  c("Sex","DOB","DOT","Order","UV1.Nao","UV2.Nao","UV3.Nao","A1.Nao","A2.Nao","IS1.Nao","IS2.Nao","IS3.Nao","IS4.Nao","IS5.Nao","IS6.Nao","HL1.Nao","E1.Nao","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")) {
  
  UV[[var]] = safe.ifelse(is.na(UV.Total[[paste(var,".x",sep="")]]),
                          UV.Total[[paste(var,".y",sep="")]],
                          UV.Total[[paste(var,".x",sep="")]])
}

```

##Age Breakdown
```{r calculate_variables}
#library lubridate
#calculate age of participant in months
UV$Age = (year(as.period(interval(UV$DOB, UV$DOT)))*12) + month(as.period(interval(UV$DOB, UV$DOT))) + (day(as.period(interval(UV$DOB, UV$DOT)))/30)
UV$Age.C = as.numeric(scale(UV$Age,center=T,scale=T))

#calculate age of participant in years
UV$AgeYears = UV$Age/12

#separate into age groups variables
UV$AgeGroup2 = factor(ifelse(UV$Age<mean(UV$Age), "1", "2"))
UV$AgeGroup3 = factor(ifelse(UV$Age<96, "1", ifelse(UV$Age<144, "2", "3")))
UV$AgeGroup4 = factor(ifelse(UV$Age<72, "1", ifelse(UV$Age<108, "2", ifelse(UV$Age<144, "3", "4"))))
UV$AgeGroup5 = factor(ifelse(UV$Age<72, "1", ifelse(UV$Age<96, "2", ifelse(UV$Age<120, "3", ifelse(UV$Age<144, "4", "5")))))


UV = UV[which(UV$AgeYears>=1),]

#pander(table(UV$AgeGroup4))
#pander(table(UV$AgeGroup4,UV$Sex))
#pander(aggregate(UV$AgeYears,list(UV$AgeGroup4),mean))
#pander(aggregate(UV$AgeYears,list(UV$AgeGroup4),min))
#pander(aggregate(UV$AgeYears,list(UV$AgeGroup4),max))

ggplot(UV, aes(x=AgeYears)) + geom_histogram()
```


##Exploratory factor analysis for Kaspar Back
Factor analysis with nonorthogonal oblimin rotation
```{r EFA_Back}
#reverse code
UV$UV3.Back.r = recode(UV$UV3.Back, '1=4; 2=3; 3=2; 4=1')

#factor analysis with all variables for machine-like robot
#Q.Back <- c("UV1.Back","UV2.Back","UV3.Back.r","A1.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back","IS4.Back", "IS5.Back","IS6.Back","E1.Back","HL1.Back")

#create scree plot
#efa.QB <- fa(na.omit(UV[Q.Back]), nfactors=4, rotate="oblimin",fm="pa")
#screeplot.factanal(efa.QB)

#efa.QB <- fa(na.omit(UV[Q.Back]), nfactors=3, rotate="oblimin",fm="pa")

#display factor loadings
#print(efa.QB, digits=2, sort=TRUE)

#remove cross-loading or low-loading variables: IS4.back (cross), E1.back (cross), A1.back(cross), HL1.back(low) 
Q.Back <- c("UV1.Back","UV2.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back", "IS5.Back","IS6.Back")

efa.QB <- fa(na.omit(UV[Q.Back]), nfactors=3, rotate = "geominQ", fm="minres", max.iter=10000)
#print(efa.QB, digits=2, sort=TRUE)

back.RMSEA = round(efa.QB$RMSEA["RMSEA"],4)
back.RMSEA.lower = round(efa.QB$RMSEA["lower"],4)
back.RMSEA.upper = round(efa.QB$RMSEA["upper"],4)

back.TLI = efa.QB$TLI

back.chi = round(efa.QB$STATISTIC,4)
back.chi.df = efa.QB$dof
back.chi.p = round(efa.QB$PVAL,3)

#create three factors
back.factor1 <- c("IS1.Back","IS2.Back","A2.Back") #think, moral, choose
back.factor2 <- c("IS3.Back","IS5.Back","IS6.Back") #pain,fear,hunger
#back.factor3 <- c("UV1.Back","UV2.Back","UV3.Back.r")

#calculate alpha for each factor
a.back.factor1 = psych::alpha(UV[back.factor1]) #alpha = 0.72 (.66,.78), #agency
a.back.factor2 = psych::alpha(UV[back.factor2]) #alpha = 0.73 (.67, .79), #experience
#a.back.factor3 = psych::alpha(UV[back.factor3],check.keys=TRUE) #alpha = 0.7 (.64,.77), uv
r = cor(UV$UV1.Back,UV$UV2.Back,use="complete.obs",method="spearman")
a.back.factor3 = (2*r)/(1+r)

round(as.table(efa.QB$loadings),2)
```

##Exploratory factor analysis for Kaspar Front
Factor analysis with nonorthogonal oblimin rotation
```{r EFA_Front}
UV$UV3.Front.r = recode(UV$UV3.Front, '1=4; 2=3; 3=2; 4=1')

#factor analysis with all variables for machine-like robot
#Q.Front <- c("UV1.Front","UV2.Front","UV3.Front.r","A1.Front","A2.Front","IS1.Front","IS2.Front","IS3.Front","IS4.Front", "IS5.Front","IS6.Front","E1.Front","HL1.Front")

#create scree plot
#efa.QF <- fa(na.omit(UV[Q.Front]), nfactors=3, rotate="oblimin", fm="pa")
#screeplot.factanal(efa.QF)

#display factor loadings
#print(efa.QF, digits=2, sort=TRUE)

#remove cross-loading or low-loading variables: IS4.Front (cross), HL1.Front (low)
Q.Front <- c("UV1.Front","UV2.Front","IS1.Front","A2.Front","IS2.Front","IS3.Front","IS5.Front","IS6.Front")

efa.QF <- fa(na.omit(UV[Q.Front]), nfactors=3, rotate = "geominQ", fm="minres", max.iter=10000)

#screeplot.factanal(efa.QF)

#print(efa.QF, digits=2, sort=TRUE)

front.RMSEA = round(efa.QF$RMSEA["RMSEA"],4)
front.RMSEA.lower = round(efa.QF$RMSEA["lower"],4)
front.RMSEA.upper = round(efa.QF$RMSEA["upper"],4)

front.TLI = efa.QF$TLI

front.chi = round(efa.QF$STATISTIC,4)
front.chi.df = efa.QF$dof
front.chi.p = round(efa.QF$PVAL,3)

#create recommended factors
front.factor2 <- c("IS3.Front","IS5.Front","IS6.Front") #pain,fear,hunger 
front.factor1 <- c("IS1.Front","A2.Front", "IS2.Front") #think, moral, choose
#front.factor3 <- c("UV1.Front","UV2.Front","UV3.Front.r")

#calculate alpha for each factor
a.front.factor1 = psych::alpha(UV[front.factor1]) #alpha = .85 (.82,.88), experience
a.front.factor2 = psych::alpha(UV[front.factor2]) #alpha = .64 (.57,.72), agency
#a.front.factor3 = psych::alpha(UV[front.factor3]) #alpha = .65 (.57,.73) (if drop UV3 -> .74), uv
r = cor(UV$UV1.Front,UV$UV2.Front,use="complete.obs",method="spearman")
a.front.factor3 = (2*r)/(1+r)

round(as.table(efa.QF$loadings),2)
```

##Exploratory factor analysis for Nao
Factor analysis with nonorthogonal oblimin rotation
```{r EFA_Nao}

UV$UV3.Nao.r = recode(UV$UV3.Nao, '1=4; 2=3; 3=2; 4=1')

#factor analysis with all variables for machine-like robot
#Q.Nao <- c("UV1.Nao","UV2.Nao","A1.Nao","A2.Nao","IS1.Nao","IS2.Nao","IS3.Nao","IS4.Nao", "IS5.Nao","IS6.Nao","E1.Nao","HL1.Nao")

#create scree plot
#efa.QN <- fa(na.omit(UV[Q.Nao]), nfactors=2, rotate="promax", fm="pa")
#screeplot.factanal(efa.QN)

#display factor loadings
#print(efa.QN, digits=2, sort=TRUE)

#remove cross-loading or low-loading variables: IS4.Nao (cross), HL1.Nao (low)
Q.Nao <- c("UV1.Nao","UV2.Nao","IS1.Nao","A2.Nao","IS2.Nao","IS3.Nao", "IS5.Nao","IS6.Nao")

efa.QN <- fa(na.omit(UV[Q.Nao]), nfactors=3, rotate="geominQ", fm="minres", max.iter=10000)
#screeplot.factanal(efa.QN)

#print(efa.QN, digits=2, sort=TRUE)

Nao.RMSEA = round(efa.QN$RMSEA["RMSEA"],4)
Nao.RMSEA.lower = round(efa.QN$RMSEA["lower"],4)
Nao.RMSEA.upper = round(efa.QN$RMSEA["upper"],4)

Nao.TLI = efa.QN$TLI

Nao.chi = round(efa.QN$STATISTIC,4)
Nao.chi.df = efa.QN$dof
Nao.chi.p = round(efa.QN$PVAL,3)

#create recommended factors
Nao.factor2 <- c("IS3.Nao","IS5.Nao","IS6.Nao","IS1.Nao","A2.Nao", "IS2.Nao") #pain,fear,hunger 
Nao.factor1 <- c("IS1.Nao","A2.Nao", "IS2.Nao") #think, moral, choose
#Nao.factor3 <- c("UV1.Nao","UV2.Nao","UV3.Nao.r")

#calculate alpha for each factor
a.Nao.factor1 = psych::alpha(UV[Nao.factor1]) #alpha = .85 (.82,.88), experience
a.Nao.factor2 = psych::alpha(UV[Nao.factor2]) #alpha = .64 (.57,.72), agency
#a.Nao.factor3 = psych::alpha(UV[Nao.factor3]) #alpha = .65 (.57,.73) (if drop UV3 -> .74), uv

r = cor(UV$UV1.Nao,UV$UV2.Nao,use="complete.obs",method="spearman")
a.Nao.factor3 = (2*r)/(1+r)

round(as.table(efa.QN$loadings),3)
```

```{r}
pander(data.frame("Robot" = c("Machine","Human","Nao"), 
           "RMSEA" = c(paste(back.RMSEA," (",back.RMSEA.lower,",",back.RMSEA.upper,")",sep=""),
                       paste(front.RMSEA," (",front.RMSEA.lower,",",front.RMSEA.upper,")",sep=""),
                       paste(Nao.RMSEA," (",Nao.RMSEA.lower,",",Nao.RMSEA.upper,")",sep="")),
           "TLI" = c(back.TLI, front.TLI, Nao.TLI),
           "Chi-squared" = c(paste(back.chi,"(", back.chi.df,")",sep=""),
                             paste(front.chi,"(",front.chi.df,")",sep=""),
                             paste(Nao.chi,"(", Nao.chi.df, ")",sep="")),
           "Chi-square (>p)" = c(back.chi.p, front.chi.p, Nao.chi.p)))

pander(data.frame("Robot" = c("Machine", "Human", "Nao"), 
                  "Agency" = c(a.back.factor1$total$raw_alpha, 
                               a.front.factor1$total$raw_alpha, 
                               a.Nao.factor1$total$raw_alpha),
                  "Experience" = c(a.back.factor2$total$raw_alpha,
                                   a.front.factor2$total$raw_alpha,
                                   a.Nao.factor2$total$raw_alpha),
                  "UV" = c(a.back.factor3,
                           a.front.factor3,
                           a.Nao.factor3)))
                  #"UV" = c(a.back.factor3$total$raw_alpha,
                  #         a.front.factor3$total$raw_alpha,
                  #         a.Nao.factor3$total$raw_alpha)))
```

```{r aggregates}
efa.QB.scores = as.data.frame(efa.QB$scores)
efa.QF.scores = as.data.frame(efa.QF$scores)
efa.QN.scores = as.data.frame(efa.QN$scores)

names(efa.QB.scores) = c("Ag.score.back","Exp.score.back","UV.score.back")
names(efa.QF.scores) = c("Exp.score.front","UV.score.front","Ag.score.Front")
names(efa.QN.scores) = c("Exp.score.Nao","Ag.score.Nao","UV.score.Nao")

#names(efa.QB.scores) = c("Mind.score.back","UV.score.back")
#names(efa.QF.scores) = c("Mind.score.front","UV.score.front")
#names(efa.QN.scores) = c("Mind.score.Nao","UV.score.Nao")

UV = merge(UV, efa.QB.scores, by = 0, all.x=T)
UV$Row.names = NULL
UV = merge(UV, efa.QF.scores, by = 0, all.x=T)
UV$Row.names = NULL
UV = merge(UV, efa.QN.scores, by = 0, all.x=T)
UV$Row.names = NULL

UV$UVindex3.Back = (UV$UV1.Back+UV$UV2.Back+UV$UV3.Back.r)/3
UV$UVindex2.Back = (UV$UV1.Back+UV$UV2.Back)/2
UV$Agency.Back = (UV$A2.Back+UV$IS1.Back+UV$IS2.Back)/3
UV$Exp.Back = (UV$IS3.Back+UV$IS5.Back+UV$IS6.Back)/3
UV$Mind.Back = (UV$A2.Back+UV$IS1.Back+UV$IS2.Back+UV$IS3.Back+UV$IS5.Back+UV$IS6.Back)/6

UV$UVindex3.Front = (UV$UV1.Front+UV$UV2.Front+UV$UV3.Front.r)/3
UV$UVindex2.Front = (UV$UV1.Front+UV$UV2.Front)/2
UV$Agency.Front = (UV$A2.Front+UV$IS1.Front+UV$IS2.Front)/3
UV$Exp.Front = (UV$IS3.Front+UV$IS5.Front+UV$IS6.Front)/3
UV$Mind.Front = (UV$A2.Front+UV$IS1.Front+UV$IS2.Front+UV$IS3.Front+UV$IS5.Front+UV$IS6.Front)/6

UV$UVindex3.Nao = (UV$UV1.Nao+UV$UV2.Nao+UV$UV3.Nao.r)/3
UV$UVindex2.Nao = (UV$UV1.Nao+UV$UV2.Nao)/2
UV$Agency.Nao = (UV$A2.Nao+UV$IS1.Nao+UV$IS2.Nao)/3
UV$Exp.Nao = (UV$IS3.Nao+UV$IS5.Nao+UV$IS6.Nao)/3
UV$Mind.Nao = (UV$A2.Nao+UV$IS1.Nao+UV$IS2.Nao+UV$IS3.Nao+UV$IS5.Nao+UV$IS6.Nao)/6
```

```{r reformat_data}
#Order==1 is Back
#Order==2 is Front
UV$UV3 = NA
UV$UV2 = NA
UV$Agency = NA
UV$Exp = NA
UV$Mind = NA
UV$UVscore = NA
UV$AGscore = NA
UV$EXPscore = NA

UV$UVscore[which(UV$Order==2)] = UV$UV.score.front[which(UV$Order==2)]
UV$UVscore[which(UV$Order==1)] = UV$UV.score.back[which(UV$Order==1)]

UV$AGscore[which(UV$Order==2)] = UV$Ag.score.Front[which(UV$Order==2)]
UV$AGscore[which(UV$Order==1)] = UV$Ag.score.back[which(UV$Order==1)]

UV$EXPscore[which(UV$Order==2)] = UV$Exp.score.front[which(UV$Order==2)]
UV$EXPscore[which(UV$Order==1)] = UV$Exp.score.back[which(UV$Order==1)]

#UV$MINDscore[which(UV$Order==2)] = UV$Mind.score.front[which(UV$Order==2)]
#UV$MINDscore[which(UV$Order==1)] = UV$Mind.score.back[which(UV$Order==1)]

UV$UV3[which(UV$Order==2)] = UV$UVindex3.Front[which(UV$Order==2)]
UV$UV3[which(UV$Order==1)] = UV$UVindex3.Back[which(UV$Order==1)]

UV$UV2[which(UV$Order==2)] = UV$UVindex2.Front[which(UV$Order==2)]
UV$UV2[which(UV$Order==1)] = UV$UVindex2.Back[which(UV$Order==1)]

UV$Agency[which(UV$Order==2)] = UV$Agency.Front[which(UV$Order==2)]
UV$Agency[which(UV$Order==1)] = UV$Agency.Back[which(UV$Order==1)]

UV$Exp[which(UV$Order==2)] = UV$Exp.Front[which(UV$Order==2)]
UV$Exp[which(UV$Order==1)] = UV$Exp.Back[which(UV$Order==1)]

UV$Mind[which(UV$Order==2)] = UV$Mind.Front[which(UV$Order==2)]
UV$Mind[which(UV$Order==1)] = UV$Mind.Back[which(UV$Order==1)]

```


```{r regressions}

#UV$UV3.log = log10(UV$UV)
#UV$UV2.log = log10(UV$UV2)
#UV$UV3.C = scale(UV$UV,center = T,scale = T)
UV$Agency.C = scale(UV$Agency,center = T, scale = T)
UV$Exp.C = scale(UV$Exp,center = T, scale = T)
UV$Mind.C = scale(UV$Mind, center = T, scale = T)

UV$AGscore.C = scale(UV$AGscore, center = T, scale = T)
UV$EXPscore.C = scale(UV$EXPscore, center = T, scale = T)
UV$MINDscore.C = scale((UV$AGscore+UV$EXPscore)/2,center=T,scale=T)
#UV$UV3.Nao.C = scale(UV$UV3.Nao,center = T, scale = T)
#UV$UV2.Nao.C = scale(UV$UV2.Nao,center = T, scale = T)
#UV$Age.pwr2 = UV$Age.C^2
#UV$Age.pwr3 = UV$Age.C^3

UV$Robot = ifelse(UV$Order==1," Machine-like"," Human-like")
UV$Robot = factor(UV$Robot,levels(factor(UV$Robot))[c(2,1)])

UV$UV3.diff = UV$UV3-UV$UVindex3.Nao
UV$UV2.diff = UV$UV2-UV$UVindex2.Nao
UV$UVscore.diff = UV$UVscore-UV$UV.score.Nao

lm.out = lm(UV2.diff~Robot*Age.C+Mind.C*Age.C,
            data=UV)
pander(summary(lm.out), caption = "full sample regression")
pander(lm.beta(lm.out))
```

```{r moderation}
#Y = UV2.diff
#moderator = Age
#X = Robot

UV$RobotXAge = as.numeric(UV$Robot)*UV$Age.C
UV$MindXAge = UV$Mind.C*UV$Age.C

lm.out = lm(UV2.diff~Robot+Age.C+Mind.C+RobotXAge+MindXAge,data=UV)
summary(lm.out)

model <- '
  ## Direct effects
  UV2.diff ~ c1*Robot
  UV2.diff ~ c2*Age.C
  UV2.diff ~ c3*Mind.C
  UV2.diff ~ c4*RobotXAge
  UV2.diff ~ c5*MindXAge
  ## Conditional direct effect
  rob.4years := c1 + c4*-1.5 # 4 years
  rob.6years := c1 + c4*-.85 # 6 years
  rob.8years := c1 + c4*-.2 # 8 years
  rob.9years := c1 + c4*.1355521733 # 9 years exactly
  rob.10years := c1 + c4*.45 # 10 years
  rob.12years := c1 + c4*1.1 # 12 years
  rob.14years := c1 + c4*1.75 # 14 years
  rob.16years := c1 + c4*2.4 # 16 years
  mind.4years := c3 + c5*-1.5 # 4 years
  mind.6years := c3 + c5*-.85 # 6 years
  mind.8years := c3 + c5*-.2 # 8 years
  mind.9years := c3 + c5*.1355521733 # 9 years exactly
  mind.10years := c3 + c5*.45 # 10 years
  mind.12years := c3 + c5*1.1 # 12 years
  mind.14years := c3 + c5*1.75 # 14 years
  mind.16years := c3 + c5*2.4 # 16 years
  '
         
fit <- sem(model, data = UV, se = "bootstrap", test = "bootstrap")
summary(fit, standardized = TRUE, rsq = TRUE)
parameterEstimates(fit)
```

```{r, fig.height=6,fig.width=6.5}
lm.out.back = lm(UV2.diff~AgeYears,
            data=UV[UV$Order==1,])
lm.out.front = lm(UV2.diff~AgeYears,
            data=UV[UV$Order==2,])

agevalues <- seq(3.1111, 17.6111, length.out = 239)
p.back <- predict(lm.out.back,list(AgeYears = agevalues))
p.front <- predict(lm.out.front,list(AgeYears = agevalues))
{par(pty="s")
  plot(jitter(UV$AgeYears),
       jitter(UV$UV2.diff),
       pch=20,
       col=scales::alpha(ifelse(UV$Order==1,"red","blue"),.5),
       ylab="Uncanniness Difference Scores",
       xlab = "Age (Years)")
  lines(agevalues, p.back, col = "red", lwd = 3)
  lines(agevalues, p.front, col = "blue", lwd = 3)
  legend(x = 12.75,
         y = -2.25, 
         c('Machine-Like','Human-Like'),
         lty=c(1,1),
         lwd=c(3,3),
         col=c("red","blue"),
         cex = .75)}

#geom_line(data=dataset, aes_string(x=varx, y=vary))
#theme(aspect.ratio=1)

lm.out = lm(UV2.diff~AgeYears*Order,data=UV)
pander(summary(lm.out), caption = "full sample regression")

pander(lm.beta(lm.out))
```

```{r, fig.height=6,fig.width=6.5}
lm.out.young = lm(UV2.diff~Mind,
            data=UV[UV$AgeYears<10,])
lm.out.old = lm(UV2.diff~Mind,
            data=UV[UV$AgeYears>=10,])

mindvalues <- seq(1, 4, length.out = 239)
p.young <- predict(lm.out.young,list(Mind = mindvalues))
p.old <- predict(lm.out.old,list(Mind = mindvalues))
{par(pty="s")
  plot(jitter(UV$Mind),
       jitter(UV$UV2.diff),
       pch=20,
       col=scales::alpha(ifelse(UV$AgeYears<10,"red","blue"),.5),
       ylab="Uncanniness Difference Scores",
       xlab = "Attributions of Mind")
  lines(mindvalues, p.young, col = "red", lwd = 3)
  lines(mindvalues, p.old, col = "blue", lwd = 3)
  legend(x=3,
         y=-2.25, 
         c('Younger than 10','10 and older'),
         lty=c(1,1),
         lwd=c(3,3),
         col=c("red","blue"),
         cex=.75)}

#geom_line(data=dataset, aes_string(x=varx, y=vary))
#theme(aspect.ratio=1)

#lm.out = lm(UV2.diff~AgeYears*Order,data=UV)
#pander(summary(lm.out), caption = "full sample regression")

#pander(lm.beta(lm.out))
```

```{r}
uv.back = melt(UV[,c("UV2.Back","UV2.Nao","Age.C","SubID")], id=c("Age.C","SubID"))
uv.front = melt(UV[,c("UV2.Front","UV2.Nao","Age.C","SubID")], id=c("Age.C","SubID"))

uv.back = uv.back[complete.cases(uv.back),]
uv.front = uv.front[complete.cases(uv.front),]

summary(lm(value~variable*Age.C,data=uv.back))
summary(lm(value~variable*Age.C,data=uv.front))

lm.beta(lm(value~variable*Age.C,data=uv.back))
```
