---
title: "Uncanny Valley - Child Development"
author: "Kimberly A. Brink"
date: "October 23, 2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Manuscript Figures/', dev=c('png','postscript'), fig.width = 8, fig.height = 8, fig.keep='last', echo=FALSE, warning=FALSE, message=FALSE)
```

```{r libraries}
library(lubridate) #for calculating ages
library(Hmisc) #for importing SPSS
library(plyr) #for joining data frames
library(pander) #for displaying tables
library(psych)
library(QuantPsyc)
library(lsr)
library(reshape2) #melt
library(lavaan)
library(car) #reverse coding
library(wesanderson)
library(pwr)

wesanderson = "GrandBudapest2"

```

```{r standard_error}
#calculates standard error (automatically removes missing values)
std.error <- function(x) sd(x,na.rm=TRUE)/sqrt(length(x))
```

```{r ifelse_safe}
#when using the original ifelse statement, the class of the variable contained in the yes/no statements is not protected. if a variable is contained in the yes/no statement, it may be converted to an illegible numerical class. "ifelse makes factors lose their levels and Dates lose their class and only their mode (numeric) is restored"

#this ifelse.safe function came from: http://stackoverflow.com/questions/6668963/how-to-prevent-ifelse-from-turning-date-objects-into-numeric-objects

#it protects both date columns and factor columns

ifelse.safe <- function(cond, yes, no) {
      class.y <- class(yes)
      if ("factor" %in% class.y) {  
        levels.y = levels(yes)
      }
      X <- ifelse(cond,yes,no)
      if ("factor" %in% class.y) {  
        X = as.factor(X)
        levels(X) = levels.y
      } else {
        class(X) <- class.y
      }
      return(X)
}
```

```{r screeplot_factanal}
#http://www.stat.cmu.edu/~cshalizi/350/2008/lectures/14/lecture-14.pdf
screeplot.factanal <- function(fa.fit,xlab="factor",ylab="eigenvalue",...) {
	# sum-of-squares function for repeated application
	sosq <- function(v) {sum(v^2)}
	# Get the matrix of loadings
	my.loadings <- as.matrix(fa.fit$loadings)
	# Eigenvalues can be recovered as sum of
	# squares of each column
	evalues <- apply(my.loadings,2,sosq)
	plot(evalues,xlab=xlab,ylab=ylab,...)
}
```

```{r part_cor_function, echo = FALSE}
#runs a partial correlation that can handle missing values
#I think I made this. I'm sure pieces came from all over.
part.cor <- function(x, y, z){
  xres <- residuals(lm(x ~ z, na.action = na.exclude))
  yres <- residuals(lm(y ~ z, na.action = na.exclude)) 
  result <- cor.test(xres, yres) 
  m = data.frame(1)
  m$estimate = result$estimate 
  m$tvalue = result$statistic 
  m$df = result$parameter
  m$p.value = result$p.value
  return(m)
}
```

```{r barByAge_function}
barByAge <-function(v.back,v.front,v.nao,data,title){
  #find means of var for each age group for the machine-like robot
  means.back <- aggregate(v.back~AgeGroup4,data,mean)
  #find means of variable for each age group for the human-like robot
  means.front <- aggregate(v.front~AgeGroup4,data,mean) 
  #find means of variable for each age group for the human-like robot
  means.nao <- aggregate(v.nao~AgeGroup4,data,mean) 
  
  #find standard error of var for each age group for the machine-like robot
  se.back <- aggregate(v.back~AgeGroup4,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.front <- aggregate(v.front~AgeGroup4,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.nao <- aggregate(v.nao~AgeGroup4,data,std.error) 
  
  means.mat<-matrix(c(means.back$v.back,means.front$v.front,means.nao$v.nao),
                    ncol=4,
                    byrow=T)-1 #combine means into one matrix
  se.mat<-matrix(c(se.back$v.back,se.front$v.front,se.nao$v.nao),
                 ncol=4,
                 byrow=FALSE) #combine se into one matrix
  
  #label the columns by age group
  colnames(means.mat) <- c('3-5','6-8','9-11','12-18')
  colnames(se.mat) <- c('3-5','6-8','9-11','12-18')

  #label the rows by robot type
  rownames(means.mat) <- c('Machine-like','Human-like','Nao')
  rownames(se.mat) <- c('Machine-like','Human-like','Nao')

  #produce rounded values of the matrix for displaying on the plot
  means.matR <- round(means.mat,2) 

  plotData = melt(means.matR)
  seData = melt(se.mat)
  
  names(plotData) = c("Robot","Age Group",title)
  names(seData) = c("Robot","Age Group","SE")
  #title = plotData$

  plotData = join(plotData,seData)
  
  ggplot(data = plotData, aes(x = `Age Group`, y = plotData[title], fill = Robot)) + 
    geom_bar(width = .65, position=position_dodge(), stat="identity") + 
    scale_fill_grey(start=.8,end=.3) + 
    geom_errorbar(aes(ymin=plotData[title]-SE, ymax=plotData[title]+SE),
                  width=.2, #Line weights
                  size = 1, #Width of the error bars
                  position=position_dodge(.65)) + 
    labs(x="Age (years)",y=title) + 
    theme(text = element_text(size=12,family="Helvetica"), #set font
          axis.text.x = element_text(size=11), #set size of x-axis font
          axis.title.x = element_text(margin=margin(10,0,0,0), size=14), #set position of x-axis title
          axis.text.y=element_text(angle=90, hjust=.5, size=11), #set size of y-axis text
          axis.title.y=element_text(margin=margin(0,20,0,0), size=14), #set position of y-axis title
          legend.background = element_rect(), #empty box legend
          legend.key.size = unit(1, "cm"), #set size of boxes for legend
          legend.position="bottom", #set position of legend at bottom
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black")) + 
  scale_y_continuous(limits = c(0,3.15), #set min and max of y-axis
                     breaks=0:3, #set y continuous to 4 tick marks at 0,1,2,3
                     labels=c('Not at all', 'A little bit', 'A medium amount', 'A lot'), #set labels
                     expand = c(0,0))  #set y-axis at 0
  #scale_x_discrete(expand = c(0,0)) #set x-axis
}
```

```{r barByAge_color_function}
barByAge.color <-function(v.back,v.front,v.nao,data,title){
  #find means of var for each age group for the machine-like robot
  means.back <- aggregate(v.back~AgeGroup4,data,mean)
  #find means of variable for each age group for the human-like robot
  means.front <- aggregate(v.front~AgeGroup4,data,mean) 
  #find means of variable for each age group for the human-like robot
  means.nao <- aggregate(v.nao~AgeGroup4,data,mean) 
  
  #find standard error of var for each age group for the machine-like robot
  se.back <- aggregate(v.back~AgeGroup4,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.front <- aggregate(v.front~AgeGroup4,data,std.error) 
  #find standard error of var for each age group for the human-like robot
  se.nao <- aggregate(v.nao~AgeGroup4,data,std.error) 
  
  means.mat<-matrix(c(means.back$v.back,means.front$v.front,means.nao$v.nao),
                    ncol=4,
                    byrow=T)-1 #combine means into one matrix
  se.mat<-matrix(c(se.back$v.back,se.front$v.front,se.nao$v.nao),
                 ncol=4,
                 byrow=FALSE) #combine se into one matrix
  
  #label the columns by age group
  colnames(means.mat) <- c('3-5','6-8','9-11','12-18')
  colnames(se.mat) <- c('3-5','6-8','9-11','12-18')

  #label the rows by robot type
  rownames(means.mat) <- c('Machine-like','Human-like','Nao')
  rownames(se.mat) <- c('Machine-like','Human-like','Nao')

  #produce rounded values of the matrix for displaying on the plot
  means.matR <- round(means.mat,2) 

  plotData = melt(means.matR)
  seData = melt(se.mat)
  
  names(plotData) = c("Robot","Age Group",title)
  names(seData) = c("Robot","Age Group","SE")
  #title = plotData$

  plotData = join(plotData,seData)
  
  ggplot(data = plotData, aes(x = `Age Group`, y = plotData[title], fill = Robot)) + 
    geom_bar(width = .65, position=position_dodge(), stat="identity") + 
    scale_fill_manual(values=wes_palette(n=3, name=wesanderson)) +
    geom_errorbar(aes(ymin=plotData[title]-SE, ymax=plotData[title]+SE),
                  width=.2, #Line weights
                  size = 1, #Width of the error bars
                  position=position_dodge(.65)) + 
    labs(x="Age (years)",y=title) + 
    theme(text = element_text(size=12,family="Helvetica"), #set font
          axis.text.x = element_text(size=11), #set size of x-axis font
          axis.title.x = element_text(margin=margin(10,0,0,0), size=14), #set position of x-axis title
          axis.text.y=element_text(angle=90, hjust=.5, size=11), #set size of y-axis text
          axis.title.y=element_text(margin=margin(0,20,0,0), size=14), #set position of y-axis title
          legend.background = element_rect(), #empty box legend
          legend.key.size = unit(1, "cm"), #set size of boxes for legend
          legend.position="bottom", #set position of legend at bottom
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black")) + 
  scale_y_continuous(limits = c(0,3.15), #set min and max of y-axis
                     c, #set y continuous to 4 tick marks at 0,1,2,3
                     labels=c('Not at all', 'A little bit', 'A medium amount', 'A lot'), #set labels
                     expand = c(0,0))  #set y-axis at 0
  #scale_x_discrete(expand = c(0,0)) #set x-axis
  
}
```


```{r load_file}
#library Hmisc
#load SPSS data file
filename <- "/Volumes/lsa-research01/ALL STUDIES/Current Studies/Uncanny Valley/1.0/UV - Data.sav"
UV.original <- spss.get(filename,datevars=c("DOB","DOT"),use.value.labels=F) #label DOB and DOT as date variables and import numerical values not string values for variables

UV.labels <- spss.get(filename,datevars=c("DOB","DOT"),use.value.labels=T) #import string values for variables
```

```{r formatting}
#library plyr
#exclude orders 3 and where both conditions were presented together (leaving only between subjects for analysis)
UV.original <- UV.original[UV.original$Order==1|UV.original$Order==2|is.na(UV.original$Order),] 

UV.original = UV.original[which(!is.na(UV.original$SubID)),] #remove empty observations

UV.original$Age = NULL #remove experiementer entered age (will calculate later)
UV.original$AgeGroup = NULL #remove experiementer entered age (will calculate later)
UV.original$AgeYear = NULL #remove experiementer entered age (will calculate later)
UV.original$COMME0 = NULL #remove empty variable
names(UV.original)[names(UV.original) == 'VAR00001'] <- 'Comments' #name unnamed variable
names(UV.original)[names(UV.original) == 'PA11'] <- 'PQ11' #correct name of variable

#original data set was created in long format, the following code converts it to short format
#each participant had an observation for either the machine-like robot or human-like robot, then they had a set of answers about Nao. This makes sure all answers about robots are included in one observation.

#separate answers about each robot into separate data frames
UV.Nao <- UV.original[UV.original$Condition==3,] 
UV.Front <- UV.original[UV.original$Condition==2,] 
UV.Back <- UV.original[UV.original$Condition==1,] 

#remove empty observations (that would have somehow magically slipped by when I removed them before)
UV.Nao = UV.Nao[which(!is.na(UV.Nao$SubID)),] 
UV.Front = UV.Front[which(!is.na(UV.Front$SubID)),] 
UV.Back = UV.Back[which(!is.na(UV.Back$SubID)),] 

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Nao) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Nao","UV2.Nao","UV3.Nao","A1.Nao","A2.Nao","IS1.Nao","IS2.Nao","IS3.Nao","IS4.Nao","IS5.Nao","IS6.Nao","HL1.Nao","E1.Nao","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#the variables below are typically empty for Nao and not robot specific (they are a parent survey about experience with robots and technology), they can be copied over from UV.Front and UV.Back where they are always filled in
#if these variables are left in UV.Nao they cause problems with joins later
#the same subid may have empty data for these variables for the Nao dataset but not the UV.Front or UV.Back datasets, which causes these variables to be incorrectly copied over during the join
UV.Nao=UV.Nao[,!(names(UV.Nao) %in% c("Sex","DOB","DOT","Order","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments"))]

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Front) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Front","UV2.Front","UV3.Front","A1.Front","A2.Front","IS1.Front","IS2.Front","IS3.Front","IS4.Front","IS5.Front","IS6.Front","HL1.Front","E1.Front","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#rename variables for consistency and differentiation for when they are joined back together
names(UV.Back) <- c("SubID","Sex","DOB","DOT","Order","Condition","UV1.Back","UV2.Back","UV3.Back","A1.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back","IS4.Back","IS5.Back","IS6.Back","HL1.Back","E1.Back","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")

#condition is no longer needed (this information is kept in the variable names)
UV.Nao$Condition = NULL
UV.Back$Condition = NULL
UV.Front$Condition = NULL

UV.NB <- join( UV.Back,UV.Nao ) #combine observations about Nao and observations about the machine-like robot by subject ID
UV.NF <- join( UV.Front,UV.Nao ) #combine observations about Nao and observations about the machine-like robot by subject ID
UV.Total <- merge( UV.NB,UV.NF,by="SubID",all.x=T,all.y=T ) #put all the observations together into one data frame

#copy over variables that do not have a ".x" or ".y" on their name
UV = UV.Total[c("SubID","UV1.Front","UV2.Front","UV3.Front","A1.Front","A2.Front","IS1.Front","IS2.Front","IS3.Front","IS4.Front","IS5.Front","IS6.Front","HL1.Front","E1.Front","UV1.Back","UV2.Back","UV3.Back","A1.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back","IS4.Back","IS5.Back","IS6.Back","HL1.Back","E1.Back")]

#copy over variables with a ".x" or ".y" but remove that from the end of the variable name
for (var in  c("Sex","DOB","DOT","Order","UV1.Nao","UV2.Nao","UV3.Nao","A1.Nao","A2.Nao","IS1.Nao","IS2.Nao","IS3.Nao","IS4.Nao","IS5.Nao","IS6.Nao","HL1.Nao","E1.Nao","PQ1","PQ2","PQ3","PQ4","PQ5","PQ6","PQ7","PQ8","PQ9","PQ10","PQ11","PQ12","PQ13","PQ14","PQ15a","PQ15b","PQ16","Comments")) {
  
  UV[[var]] = ifelse.safe(is.na(UV.Total[[paste(var,".x",sep="")]]),
                          UV.Total[[paste(var,".y",sep="")]],
                          UV.Total[[paste(var,".x",sep="")]])
}

```

```{r calculate_age_variables}
#library lubridate
#calculate age of participant in months
UV$Age = (year(as.period(interval(UV$DOB, UV$DOT)))*12) + month(as.period(interval(UV$DOB, UV$DOT))) + (day(as.period(interval(UV$DOB, UV$DOT)))/30)
UV$Age.C = as.numeric(scale(UV$Age,center=T,scale=T))

#calculate age of participant in years
UV$AgeYears = UV$Age/12

#separate into age groups variables for figure 5
UV$AgeGroup2 = factor(ifelse(UV$Age<mean(UV$Age), "1", "2"))
UV$AgeGroup3 = factor(ifelse(UV$Age<96, "1", ifelse(UV$Age<144, "2", "3")))
UV$AgeGroup4 = factor(ifelse(UV$Age<72, "1", ifelse(UV$Age<108, "2", ifelse(UV$Age<144, "3", "4"))))
UV$AgeGroup5 = factor(ifelse(UV$Age<72, "1", ifelse(UV$Age<96, "2", ifelse(UV$Age<120, "3", ifelse(UV$Age<144, "4", "5")))))
```

#Method
##Participants
`r length(UV$SubID)` participants (`r sum(UV$Sex==1)` females), `r round(min(UV$AgeYears[which(UV$AgeYears>1)]))` to `r round(max(UV$AgeYears))` years old, were recruited.

Data was collected from `r min(UV$DOT)` to `r max(UV$DOT)`.

```{r exclude}
UV = UV[which(UV$AgeYears>1),]
```

`r length(UV$SubID)` remaining after removing one child with incorrect birthdate

`r sum(UV$Order==2)` children watched human-like robot

`r sum(UV$Order==1)` children watched machine-like robot

`r sum(UV$SubID %in% UV.Nao$SubID)` children watched Nao

##Power
```{r power_analysis}
#effect size Gray & Wegner
# mean difference divided by pooled SD
effect.size.uv = (1.77-1.32)/((.8+.57)/2) #uncanny valley effect

std.dev = ((.42-0)*sqrt(111))/4.3
effect.size.exp =  (.42-0)/std.dev #experience slope

#u = numerator degrees of freedom (p-1)
#v = denominator degrees of freedom (n-p)
#f2 = effect size (.02 - small, .15 - medium)
#sig.level = significance level (.05)

power = pwr.f2.test(u = 7-1, v= 240-7,f2 =effect.size.uv, sig.level = .05)

```

With a sample of 240 and 7 predictor variables, you should be able to detect the effect of robot on uncanny responses with a power of `r power$power` (should be greater than .8).


##Exploratory Factor Analysis
```{r EFA_Back_Final}
#remove cross-loading or low-loading variables: IS4.back (cross), E1.back (cross), A1.back(cross), HL1.back(low) 
Q.Back <- c("UV1.Back","UV2.Back","A2.Back","IS1.Back","IS2.Back","IS3.Back", "IS5.Back","IS6.Back")

#perform EFA
efa.QB <- fa(na.omit(UV[Q.Back]), nfactors=3, rotate = "geominQ", fm="minchi", max.iter=10000)
#h2 are communalities and should be less than 1 (when printing efa.qb)

#calculate model fit indices
#calculate RMSEA
back.RMSEA = round(efa.QB$RMSEA["RMSEA"],4)
back.RMSEA.lower = round(efa.QB$RMSEA["lower"],4)
back.RMSEA.upper = round(efa.QB$RMSEA["upper"],4)

#calculate TLI
back.TLI = efa.QB$TLI

#calculate chi-statistic
back.chi = round(efa.QB$STATISTIC,4)
back.chi.df = efa.QB$dof
back.chi.p = round(efa.QB$PVAL,3)

#create recommended factors in order to calculate reliability
back.agency <- c("IS1.Back","IS2.Back","A2.Back") #think, moral, choose
back.exp <- c("IS3.Back","IS5.Back","IS6.Back") #pain,fear,hunger

#calculate reliability for each factor
a.back.agency = psych::alpha(UV[back.agency]) #alpha = 0.72 (.66,.78), #agency
a.back.exp = psych::alpha(UV[back.exp]) #alpha = 0.73 (.67, .79), #experience
r = cor(UV$UV1.Back,UV$UV2.Back,use="complete.obs",method="spearman")
a.back.uv = (2*r)/(1+r)

#print factor loadings
back.efa = round(as.table(efa.QB$loadings),2)
```

```{r EFA_Front_Final}
#remove cross-loading or low-loading variables: IS4.Front (cross), HL1.Front (low)
Q.Front <- c("UV1.Front","UV2.Front","IS1.Front","A2.Front","IS2.Front","IS3.Front","IS5.Front","IS6.Front")

#perform EFA
efa.QF <- fa(na.omit(UV[Q.Front]), nfactors=3, rotate = "geominQ", fm="minchi", max.iter=10000)
#h2 are communalities and should be less than 1 (when printing efa.QF)

#calculate model fit indices
#calculate RMSEA
front.RMSEA = round(efa.QF$RMSEA["RMSEA"],4)
front.RMSEA.lower = round(efa.QF$RMSEA["lower"],4)
front.RMSEA.upper = round(efa.QF$RMSEA["upper"],4)

#calculate TLI
front.TLI = efa.QF$TLI

#calculate chi-statistic
front.chi = round(efa.QF$STATISTIC,4)
front.chi.df = efa.QF$dof
front.chi.p = round(efa.QF$PVAL,3)

#create recommended factors in order to calculate reliability
front.agency <- c("IS1.Front","A2.Front", "IS2.Front") #think, moral, choose
front.exp <- c("IS3.Front","IS5.Front","IS6.Front") #pain,fear,hunger 


#calculate reliability for each factor
a.front.agency = psych::alpha(UV[front.agency]) #alpha = .64 (.57,.72), agency
a.front.exp = psych::alpha(UV[front.exp]) #alpha = .85 (.82,.88), experience
r = cor(UV$UV1.Front,UV$UV2.Front,use="complete.obs",method="spearman")
a.front.uv = (2*r)/(1+r)

#print factor loadings
front.efa = round(as.table(efa.QF$loadings),2)
```

###Reliability
```{r alphas}
pander(data.frame("Robot" = c("Machine", "Human"),
                  "UV" = round(c(a.back.uv,
                           a.front.uv),2),
                  "Agency" = round(c(a.back.agency$total$raw_alpha, 
                               a.front.agency$total$raw_alpha),2),
                  "Experience" = round(c(a.back.exp$total$raw_alpha,
                                   a.front.exp$total$raw_alpha),2)))
```
###Factor Loadings Table
```{r factor_loadings}
pander(t(data.frame("Factor" = c("Uncanniness","Agency","Experience"),
                    "Creepy" = c(paste(back.efa['UV1.Back','MC2'],front.efa['UV1.Front','MC1'], sep=", "),
                                 "",
                                 ""),
                    "Weird" = c(paste(back.efa['UV2.Back','MC2'],front.efa['UV2.Front','MC1'], sep=", "),
                                "",
                                ""),
                    "Choose" = c("",
                                 paste(back.efa['A2.Back','MC3'],front.efa['A2.Front','MC3'], sep=", "),
                                 ""),
                    "Think" = c("",
                                paste(back.efa['IS1.Back','MC3'],front.efa['IS1.Front','MC3'], sep=", "),
                                ""),
                    "Moral" = c("",
                                paste(back.efa['IS2.Back','MC3'],front.efa['IS2.Front','MC3'], sep=", "),
                                ""),
                    "Pain" = c("",
                               "",
                               paste(back.efa['IS3.Back','MC1'],front.efa['IS3.Front','MC2'], sep=", ")),
                    "Fear" = c("",
                               "",
                               paste(back.efa['IS5.Back','MC1'],front.efa['IS5.Front','MC2'], sep=", ")),
                    "Hunger" = c("",
                                 "",
                                 paste(back.efa['IS6.Back','MC1'],front.efa['IS6.Front','MC2'], sep=", ")))))
```

###Model Fit Indices Table
```{r model_fit_indices}
pander(data.frame("Robot" = c("Machine","Human"),
                  "Chi-squared" = c(paste(back.chi,"(", back.chi.df,")",sep=""),
                             paste(front.chi,"(",front.chi.df,")",sep="")),
                  "Chi-square (>p)" = c(back.chi.p, front.chi.p),
                  "RMSEA" = c(paste(back.RMSEA," (",back.RMSEA.lower,",",back.RMSEA.upper,")",sep=""),
                       paste(front.RMSEA," (",front.RMSEA.lower,",",front.RMSEA.upper,")",sep="")),
                  "TLI" = c(back.TLI, front.TLI)))
```

```{r aggregates}
UV$UVindex2.Back = (UV$UV1.Back+UV$UV2.Back)/2
UV$Agency.Back = (UV$A2.Back+UV$IS1.Back+UV$IS2.Back)/3
UV$Exp.Back = (UV$IS3.Back+UV$IS5.Back+UV$IS6.Back)/3
UV$Mind.Back = (UV$A2.Back+UV$IS1.Back+UV$IS2.Back+UV$IS3.Back+UV$IS5.Back+UV$IS6.Back)/6

UV$UVindex2.Front = (UV$UV1.Front+UV$UV2.Front)/2
UV$Agency.Front = (UV$A2.Front+UV$IS1.Front+UV$IS2.Front)/3
UV$Exp.Front = (UV$IS3.Front+UV$IS5.Front+UV$IS6.Front)/3
UV$Mind.Front = (UV$A2.Front+UV$IS1.Front+UV$IS2.Front+UV$IS3.Front+UV$IS5.Front+UV$IS6.Front)/6

UV$UVindex2.Nao = (UV$UV1.Nao+UV$UV2.Nao)/2
UV$Agency.Nao = (UV$A2.Nao+UV$IS1.Nao+UV$IS2.Nao)/3
UV$Exp.Nao = (UV$IS3.Nao+UV$IS5.Nao+UV$IS6.Nao)/3
UV$Mind.Nao = (UV$A2.Nao+UV$IS1.Nao+UV$IS2.Nao+UV$IS3.Nao+UV$IS5.Nao+UV$IS6.Nao)/6
```

```{r reformat_data}
#Order==1 is Back
#Order==2 is Front

UV$UV2 = NA
UV$Agency = NA
UV$Exp = NA
UV$Mind = NA

UV$UV2[which(UV$Order==2)] = UV$UVindex2.Front[which(UV$Order==2)]
UV$UV2[which(UV$Order==1)] = UV$UVindex2.Back[which(UV$Order==1)]

UV$Agency[which(UV$Order==2)] = UV$Agency.Front[which(UV$Order==2)]
UV$Agency[which(UV$Order==1)] = UV$Agency.Back[which(UV$Order==1)]

UV$Exp[which(UV$Order==2)] = UV$Exp.Front[which(UV$Order==2)]
UV$Exp[which(UV$Order==1)] = UV$Exp.Back[which(UV$Order==1)]

UV$Mind[which(UV$Order==2)] = UV$Mind.Front[which(UV$Order==2)]
UV$Mind[which(UV$Order==1)] = UV$Mind.Back[which(UV$Order==1)]
```

```{r center_aggregates}
UV$Agency.C = scale(UV$Agency,center = T, scale = T)
UV$Exp.C = scale(UV$Exp,center = T, scale = T)
UV$Mind.C = scale(UV$Mind, center = T, scale = T)
UV$Age.C = scale(UV$Age, center = T, scale = T)

UV$Robot = ifelse(UV$Order==1, "Machine-like","Human-like")
UV$Robot.C = ifelse(UV$Order==1,-1,1)

UV$UV2.diff = UV$UV2-UV$UVindex2.Nao
```

##Identifying multicollinearity
```{r multicollinearity}
x = cor.test(UV$Agency.C,UV$Exp.C)
```

r(`r x$parameter`) = `r round(x$estimate,2)`

##Reason to not use Nao as predictor in regression
```{r nao_baseline}
cor.test(UV$UV2,UV$UVindex2.Nao)
```

#Results
##Regression
```{r regression}
lm.out = lm(UV2.diff~Robot.C*Age.C+Mind.C*Age.C,data=UV)
pander(summary(lm.out))
```

```{r regression_assumptions}
#checking for violations of assumptions
#qqPlot(lm.out, main="QQ Plot")
#outlierTest(lm.out)
#leveragePlots(lm.out)
#ncvTest(lm.out)
#vif(lm.out)
#sqrt(vif(lm.out)) > 2
#durbinWatsonTest(lm.out)

#{hist(UV$UV2.diff)
#  abline(v = mean(UV$UV2.diff,na.rm=T),
#         col = "royalblue",
#         lwd = 2)
#  abline(v = median(UV$UV2.diff,na.rm=T),
#         col = "red",
#         lwd = 2)}

#hist(UV$UV2)
```

##Robot Type x Age interaction
###Tests of Simple Slopes
```{r test_of_simple_slopes}
#Y = UV2.diff
#moderator = Age
#X = Robot

UV$RobotXAge = UV$Robot.C*UV$Age.C
UV$MindXAge = UV$Mind.C*UV$Age.C

#lm.out = lm(UV2.diff~Robot+Age.C+Mind.C+RobotXAge+MindXAge,data=UV)
#summary(lm.out)

model <- '
  ## Direct effects
  UV2.diff ~ c1*Robot.C
  UV2.diff ~ c2*Age.C
  UV2.diff ~ c3*Mind.C
  UV2.diff ~ c4*RobotXAge
  UV2.diff ~ c5*MindXAge
  ## Conditional direct effects
  rob.4years := c1 + c4*-1.52 # 4 years
  rob.6years := c1 + c4*-.86 # 6 years
  rob.8years := c1 + c4*-.203051 # 8 years
  rob.9years := c1 + c4*.125849 # 9 years exactly
  rob.10years := c1 + c4*.4547489 # 10 years
  rob.12years := c1 + c4*1.116 # 12 years
  rob.14years := c1 + c4*1.75 # 14 years
  rob.16years := c1 + c4*2.448 # 16 years
  mind.4years := c3 + c5*-1.52 # 4 years
  mind.6years := c3 + c5*-.86 # 6 years
  mind.8years := c3 + c5*-.203051 # 8 years
  mind.9years := c3 + c5*.125849 # 9 years exactly
  mind.10years := c3 + c5*.4547489 # 10 years
  mind.12years := c3 + c5*1.116 # 12 years
  mind.14years := c3 + c5*1.75 # 14 years
  mind.16years := c3 + c5*2.448 # 16 years
  '
         
set.seed(9000)
fit <- sem(model, data = UV, se = "bootstrap", test = "bootstrap")
summary(fit, standardized = TRUE, rsq = TRUE)
#parameterEstimates(fit)
```


```{r format_data_long}
uv.back = melt(UV[,c("UV2.Back","UV2.Nao","Age.C","SubID")], id=c("Age.C","SubID"))
uv.front = melt(UV[,c("UV2.Front","UV2.Nao","Age.C","SubID")], id=c("Age.C","SubID"))

uv.back = uv.back[complete.cases(uv.back),]
uv.front = uv.front[complete.cases(uv.front),]
```

##Nao as baseline

###Comparing uncanny responses between Nao and Machine-Like
```{r comparing_Nao_Back}
library(nlme)

UV.mixed = melt(UV[c("UVindex2.Back","UVindex2.Nao","UVindex2.Front","Age.C","SubID")], id=c("SubID","Age.C"))
UV.mixed = UV.mixed[complete.cases(UV.mixed),]

names(UV.mixed) = c("SubID", "Age.C", "Robot", "UV")

UV.mixed$Robot = ifelse(UV.mixed$Robot=="UVindex2.Back","Machine-like",
                        ifelse(UV.mixed$Robot=="UVindex2.Front","Human-like",
                               "Nao"))

#comparing Nao to back
UV.back.mixed = UV.mixed[UV.mixed$Robot=="Machine-like"|UV.mixed$Robot=="Nao",] 

mod = lme(UV ~ Robot*Age.C, 
          random=~ 1|SubID,
          data = UV.back.mixed)
summary(mod)
```

###Comparing uncanny responses between Nao and Human-Like
```{r comparing_Nao_Front}
#comparing Nao to front
UV.front.mixed = UV.mixed[UV.mixed$Robot=="Human-like"|UV.mixed$Robot=="Nao",] 

mod = lme(UV ~ Robot*Age.C, 
          random=~ 1|SubID,
          data = UV.front.mixed)
summary(mod)
```

###Comparing differences in responses to Nao depending on which robot was shown first

```{r nao_values}
uv.nao.means = aggregate(UVindex2.Nao~Robot,UV,FUN=mean)
uv.nao.sds = aggregate(UVindex2.Nao~Robot,UV,FUN=sd)
```

Human-like (M = `r round(uv.nao.means$UVindex2.Nao[uv.nao.means$Robot=="Human-like"],2)`, SD = `r round(uv.nao.sds$UVindex2.Nao[uv.nao.sds$Robot=="Human-like"],2)`) 

Machine-like (M = `r round(uv.nao.means$UVindex2.Nao[uv.nao.means$Robot=="Machine-like"],2)`, SD = `r round(uv.nao.sds$UVindex2.Nao[uv.nao.sds$Robot=="Machine-like"],2)`) 

```{r nao_ttest}
t.test(UVindex2.Nao~Robot,UV)
```

##Creepy-Weird Interview
```{r creepy_weird}
filename <- "/Volumes/lsa-research01/ALL STUDIES/Current Studies/Uncanny Valley/1.0/UV - Creepy-Weird.csv"
CW <- read.csv(filename)

CW$DOB = as.Date(CW$DOB, format = "%m/%d/%y")
CW$DOT = as.Date(CW$DOT, format = "%m/%d/%y")

CW$Age = (year(as.period(interval(CW$DOB, CW$DOT)))*12) + month(as.period(interval(CW$DOB, CW$DOT))) + (day(as.period(interval(CW$DOB, CW$DOT)))/30)

CW$Age = CW$Age/12

creepy = sum(CW$Creepy =="spider baby")/length(CW$Creepy)
weird = sum(CW$Weird =="ducky")/length(CW$Weird)

```

`r length(unique(CW$SubID))` children, age (M = `r round(mean(CW$Age),2)`, SD  = `r round(sd(CW$Age),2)`) [`r round(min(CW$Age),2)`, `r round(max(CW$Age),2)`]

`r creepy*100`% of these young children appropriately chose the strange toy as creepy and `r weird*100`%  chose the other strange toy as making them feel weird. 

### Table 1
```{r table_1}
pander(t(data.frame("Factor" = c("Uncanniness","Agency","Experience"),
                    "Creepy" = c(paste(back.efa['UV1.Back','MC2'],front.efa['UV1.Front','MC1'], sep=", "),
                                 paste(back.efa['UV1.Back','MC3'],front.efa['UV1.Front','MC3'], sep=", "),
                                 paste(back.efa['UV1.Back','MC1'],front.efa['UV1.Front','MC2'], sep=", ")),
                    "Weird" = c(paste(back.efa['UV2.Back','MC2'],front.efa['UV2.Front','MC1'], sep=", "),
                                paste(back.efa['UV2.Back','MC3'],front.efa['UV2.Front','MC3'], sep=", "),
                                paste(back.efa['UV2.Back','MC1'],front.efa['UV2.Front','MC2'], sep=", ")),
                    "Choose" = c(paste(back.efa['A2.Back','MC2'],front.efa['A2.Front','MC1'], sep=", "),
                                 paste(back.efa['A2.Back','MC3'],front.efa['A2.Front','MC3'], sep=", "),
                                 paste(back.efa['A2.Back','MC1'],front.efa['A2.Front','MC2'], sep=", ")),
                    "Think" = c(paste(back.efa['IS1.Back','MC2'],front.efa['IS1.Front','MC1'], sep=", "),
                                paste(back.efa['IS1.Back','MC3'],front.efa['IS1.Front','MC3'], sep=", "),
                                paste(back.efa['IS1.Back','MC1'],front.efa['IS1.Front','MC2'], sep=", ")),
                    "Moral" = c(paste(back.efa['IS2.Back','MC2'],front.efa['IS2.Front','MC1'], sep=", "),
                                paste(back.efa['IS2.Back','MC3'],front.efa['IS2.Front','MC3'], sep=", "),
                                paste(back.efa['IS2.Back','MC1'],front.efa['IS2.Front','MC2'], sep=", ")),
                    "Pain" = c(paste(back.efa['IS3.Back','MC2'],front.efa['IS3.Front','MC1'], sep=", "),
                               paste(back.efa['IS3.Back','MC3'],front.efa['IS3.Front','MC3'], sep=", "),
                               paste(back.efa['IS3.Back','MC1'],front.efa['IS3.Front','MC2'], sep=", ")),
                    "Fear" = c(paste(back.efa['IS5.Back','MC2'],front.efa['IS5.Front','MC1'], sep=", "),
                               paste(back.efa['IS5.Back','MC3'],front.efa['IS5.Front','MC3'], sep=", "),
                               paste(back.efa['IS5.Back','MC1'],front.efa['IS5.Front','MC2'], sep=", ")),
                    "Hunger" = c(paste(back.efa['IS6.Back','MC2'],front.efa['IS6.Front','MC1'], sep=", "),
                                 paste(back.efa['IS6.Back','MC3'],front.efa['IS6.Front','MC3'], sep=", "),
                                 paste(back.efa['IS6.Back','MC1'],front.efa['IS6.Front','MC2'], sep=", ")),
                    "Reliability" = c(paste(round(a.back.uv,2),round(a.front.uv,2), sep=", "),
                                      paste(round(a.back.agency$total$raw_alpha,2),
                                            round(a.front.agency$total$raw_alpha,2), 
                                            sep=", "),
                                      paste(round(a.back.exp$total$raw_alpha,2),
                                            round(a.front.exp$total$raw_alpha,2), 
                                            sep=", ")))))
```

###Table 2
```{r table_2}
UV$Robot = factor(UV$Robot, levels=c("Machine-like","Human-like"))
lm.out = lm(UV2.diff~Robot*Age.C+Mind.C*Age.C,data=UV)
#lm.out = lm(UV2.diff~Robot.C*Age.C+Mind.C*Age.C,data=UV)
pander(summary(lm.out))
pander(lm.beta(lm.out))
```

###Figure 4
```{r figure_4_BW, fig.height=6,fig.width=6.5}

UV$Robot.reorder = with(UV, factor(Robot, levels = rev(levels(Robot))))

set.seed(123)
ggplot(UV, aes(y=UV2.diff, x=AgeYears)) +
  geom_jitter(width = 0.1, height = 0.1, aes(color = Robot, shape=Robot))+
  geom_smooth(method=lm,se=F,fullrange=TRUE,aes(color=Robot)) + 
  scale_shape_manual(values=c(17,16)) +
  scale_colour_grey(start=.8,end=.2) +
  labs(y = "Uncanniness Scores", x = "Age (years)", color = "Robot", shape = "Robot") + 
  scale_x_continuous(breaks = seq(3, 18, by = 3)) + 
  scale_y_continuous(breaks = seq(-3,3,by=1)) + 
  theme(text = element_text(size=12,family="Helvetica"), #set font
        axis.text.x = element_text(size=11), #set size of x-axis font
        axis.title.x = element_text(margin=margin(10,0,0,0), size=14), #set position of x-axis title
        axis.text.y=element_text(angle=90, hjust=.5, size=11), #set size of y-axis text
        axis.title.y=element_text(margin=margin(0,20,0,0), size=14), #set position of y-axis title
        #legend.title = element_blank(),
        legend.key = element_blank(),
        legend.key.size = unit(1, "cm"), #set size of boxes for legend
        legend.key.height = unit(.7, "cm"),
        legend.position = c(.85,.12),
        legend.background = element_rect(colour="black",linetype="solid"), #empty box legend
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        aspect.ratio=1)# +
  #guides(color = guide_legend(reverse = TRUE), shape = guide_legend(reverse = TRUE))


```

```{r figure_4_color, fig.height=6,fig.width=6.5}

wesanderson = "Darjeeling"

set.seed(123)
ggplot(UV, aes(y=UV2.diff, x=AgeYears)) +
  geom_jitter(width = 0.1, height = 0.1, aes(color = Robot, shape=Robot))+
  geom_smooth(method=lm,se=F,fullrange=TRUE,aes(color=Robot)) + 
  scale_shape_manual(values=c(17,16)) +
  scale_colour_manual(values=wes_palette(n=3, name=wesanderson)) +
  labs(y = "Uncanniness Scores", x = "Age (years)", color = "Robot", shape = "Robot") + 
  scale_x_continuous(breaks = seq(3, 18, by = 3)) + 
  scale_y_continuous(breaks = seq(-3,3,by=1)) + 
  theme(text = element_text(size=12,family="Helvetica"), #set font
        axis.text.x = element_text(size=11), #set size of x-axis font
        axis.title.x = element_text(margin=margin(10,0,0,0), size=14), #set position of x-axis title
        axis.text.y=element_text(angle=90, hjust=.5, size=11), #set size of y-axis text
        axis.title.y=element_text(margin=margin(0,20,0,0), size=14), #set position of y-axis title
        #legend.title = element_blank(),
        legend.key = element_blank(),
        legend.key.size = unit(1, "cm"), #set size of boxes for legend
        legend.key.height = unit(.7, "cm"),
        legend.position = c(.85,.12),
        legend.background = element_rect(colour="black",linetype="solid"), #empty box legend
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        aspect.ratio=1)# +
  #guides(color = guide_legend(reverse = TRUE), shape = guide_legend(reverse = TRUE))
```

###Figure 5
```{r figure_5_BW, fig.width=6.75,fig.height=4.5}
barByAge(UV$UVindex2.Back,UV$UVindex2.Front,UV$UVindex2.Nao,UV,"Uncanniness")
```

```{r figure_5_color, fig.width=6.75,fig.height=4.5}
barByAge.color(UV$UVindex2.Back,UV$UVindex2.Front,UV$UVindex2.Nao,UV,"Uncanniness")
```

```{r figure_5_data}
#find means of var for each age group for the machine-like robot
means.back <- aggregate(UV$UVindex2.Back~AgeGroup4,UV,mean)
#find means of variable for each age group for the human-like robot
means.front <- aggregate(UV$UVindex2.Front~AgeGroup4,UV,mean) 
#find means of variable for each age group for the human-like robot
means.nao <- aggregate(UV$UVindex2.Nao~AgeGroup4,UV,mean) 

#find standard error of var for each age group for the machine-like robot
se.back <- aggregate(UV$UVindex2.Back~AgeGroup4,UV,std.error) 
#find standard error of var for each age group for the human-like robot
se.front <- aggregate(UV$UVindex2.Front~AgeGroup4,UV,std.error) 
#find standard error of var for each age group for the human-like robot
se.nao <- aggregate(UV$UVindex2.Nao~AgeGroup4,UV,std.error) 
  
means.mat<-matrix(c(means.back$`UV$UVindex2.Back`,
                      means.front$`UV$UVindex2.Front`,
                      means.nao$`UV$UVindex2.Nao`),
                    ncol=4,
                    byrow=T)-1 #combine means into one matrix
se.mat<-matrix(c(se.back$`UV$UVindex2.Back`,
                   se.front$`UV$UVindex2.Front`,
                   se.nao$`UV$UVindex2.Nao`),
                 ncol=4,
                 byrow=FALSE) #combine se into one matrix
  
  #label the columns by age group
colnames(means.mat) <- c('3-5','6-8','9-11','12-18')
colnames(se.mat) <- c('3-5','6-8','9-11','12-18')

#label the rows by robot type
rownames(means.mat) <- c('Machine-like','Human-like','Nao')
rownames(se.mat) <- c('Machine-like','Human-like','Nao')

#produce rounded values of the matrix for displaying on the plot
means.matR <- round(means.mat,2) 

plotData = melt(means.matR)
seData = melt(se.mat)
  
names(plotData) = c("Robot","Age Group","Uncanniness")
names(seData) = c("Robot","Age Group","SE")
#title = plotData$

plotData = join(plotData,seData)
write.csv(plotData,file = "~/Dropbox/Research/Michigan/Dissertation - Robots/Presentations/Job Talk/Figure 5 Data.csv")
```

###Additional figures
```{r figure_add_BW, fig.width=6.75,fig.height=4.5}
barByAge(UV$Mind.Back,UV$Mind.Front,UV$Mind.Nao,UV,"Uncanniness")
```

```{r figure_add_color, fig.width=6.75,fig.height=4.5}
barByAge.color(UV$Mind.Back,UV$Mind.Front,UV$Mind.Nao,UV,"Uncanniness")
```

